### 2024-12-02 paper/paper.qmd
some graphs and figures

---
title: "Voices in Parliament: Analyzing Interruptions Across Gender in the Australian Political Landscape"
subtitle: "My subtitle if needed"
author: 
  - Hannah Yu
  - Rohan Alexander
thanks: "Code and data are available at: https://github.com/hannahyu07/Hansard_Interruptions"
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(arrow)
library(here)
library(rstanarm)
library(modelsummary)
library(ggplot2)
library(knitr)
library(tibble)
library(gt)
library(patchwork)

```

```{r}
#| include: false
#| warning: false
#| message: false
hansard_corpus <- read_parquet(here::here("data/02-analysis_data/cleaned_data.parquet"))
```

```{r}
#| include: false
#| warning: false
#| message: false
# View the first few rows
head(hansard_corpus)

```

```{r}
#| include: false
#| warning: false
#| message: false
summary(hansard_corpus)
```

```{r}
#| include: false
#| warning: false
#| message: false
# Calculate interruptions and speeches by gender, including rounding the proportion
interruptions_by_gender <- hansard_corpus %>%
  group_by(gender) %>%
  summarise(
    total_interruptions = sum(interject, na.rm = TRUE),
    total_speeches = n(),
    .groups = 'drop'  # Automatically drop the grouping
  ) %>%
  mutate(
    interruption_proportion = round(total_interruptions / total_speeches, 2)  # Calculate and round the proportion of interruptions
  )

# Calculate total interruptions and speeches for all genders combined, with rounding
interruptions_all <- hansard_corpus %>%
  summarise(
    total_interruptions = sum(interject, na.rm = TRUE),
    total_speeches = n()
  ) %>%
  mutate(
    gender = "All",
    interruption_proportion = round(total_interruptions / total_speeches, 2)  # Round the proportion here as well
  )

# Combine the results for specific genders and "All"
final_results <- bind_rows(interruptions_by_gender, interruptions_all)

# Print the results
print(final_results)

```

```{r}
#| echo: false
#| warning: false
#| message: false
#| tbl-cap: "Gender-Based Interruption Analysis in Parliamentary Speeches "
#| label: tbl-1

# Create a clean and professional table
final_results %>%
  gt() %>%
  tab_header(
    title = "Proportion of Interruptions by Gender",
  ) %>%
  fmt_percent(
    columns = interruption_proportion,
    decimals = 2
  ) %>%
  cols_label(
    gender = "Gender",
    total_interruptions = "Total Interruptions",
    total_speeches = "Total Speeches",
    interruption_proportion = "Interruption Proportion"
  ) %>%
  tab_style(
    style = cell_borders(sides = "all", color = "gray", weight = px(1)),
    locations = cells_body()
  ) %>%
  tab_options(
    table.font.size = px(14),
    heading.title.font.size = px(18),
    heading.subtitle.font.size = px(14),
    data_row.padding = px(5),
    table.border.top.color = "gray",
    table.border.bottom.color = "gray"
  )

```

@tbl-1 provides a clear view of the proportion of interruptions by gender across all speeches in the dataset. The results show that male speakers were interrupted more frequently (21% of speeches) compared to female speakers (18% of speeches). Interestingly, the interruption proportion for unknown gender speakers is significantly lower, at only 11%. Overall, considering all speeches regardless of gender, the interruption proportion stands at 18%. This data suggests that gender may play a role in how frequently speakers are interrupted during parliamentary sessions, with male speakers facing a higher rate of interruption. This could reflect broader dynamics of gender interaction within the parliamentary setting.

```{r}
#| include: false
#| warning: false
#| message: false
#Based on the following data it shows that in fact men seem to be interrupted more on avergae than women in the australian parliment, but this could be changed from the "unknown" category.
# Summarize interruptions by year and gender
interruptions_summary <- hansard_corpus %>%
  group_by(year, gender) %>%
  summarise(
    total_interruptions = sum(as.numeric(interject), na.rm = TRUE),
    .groups = 'drop'
  )

# Summarize total interruptions for all genders combined per year
interruptions_all <- hansard_corpus %>%
  group_by(year) %>%
  summarise(
    total_interruptions = sum(as.numeric(interject), na.rm = TRUE),
    .groups = 'drop'
  ) %>%
  mutate(
    gender = "All"
  )

# Combine gender-specific and "All" categories data
final_data <- bind_rows(interruptions_summary, interruptions_all)

```

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-1
#| fig-cap: "Yearly Interruptions in Australian Parliament by Gender"

ggplot(final_data, aes(x = year, y = total_interruptions, color = gender)) +
  geom_line(size = 1.2) +  # Thicker lines for better visibility
  geom_point(size = 2) +  # Larger points to highlight data
  labs(
    title = "Yearly Interruptions in Australian Parliament by Gender",
    x = "Year",
    y = "Total Interruptions",
    color = "Gender"
  ) +
  scale_color_brewer(palette = "Set2") +  # Use a colorblind-friendly palette
  theme_minimal(base_size = 14) +  # Adjust base font size for readability
  theme(
    legend.position = "top",  # Move legend to the top
    legend.title = element_text(size = 10, face = "bold"),  # Bold legend title
    legend.text = element_text(size = 8),  # Adjust legend text size
    plot.title = element_text(size = 14, face = "bold"),  # Bold title
    axis.title = element_text(size = 12),  # Axis title size
    axis.text = element_text(size = 11)  # Axis text size
  ) +
  scale_x_continuous(breaks = seq(min(final_data$year), max(final_data$year), by = 5))  # Adjust x-axis breaks

```

```{r}
#| include: false
#| warning: false
#| message: false

# Ensure that 'date' is correctly formatted as Date and 'year' is extracted
hansard_corpus <- hansard_corpus %>%
  mutate(
    date = as.Date(date, format = "%Y-%m-%d"),  # Convert date if it's in character form
    year = if_else(is.na(date), NA_integer_, year(date))  # Extract year, handle NA dates
  )

# Assuming hansard_corpus has the year extracted already. If not, add this in the mutate step.
interruptions_by_year_gender <- hansard_corpus %>%
  group_by(year, gender) %>%
  summarise(
    total_interruptions = sum(interject, na.rm = TRUE),
    total_speeches = n(),
    .groups = 'drop'
  ) %>%
  mutate(
    interruption_proportion = total_interruptions / total_speeches
  )

# Calculate for all genders per year
interruptions_by_year_all <- hansard_corpus %>%
  group_by(year) %>%
  summarise(
    total_interruptions = sum(interject, na.rm = TRUE),
    total_speeches = n(),
    .groups = 'drop'
  ) %>%
  mutate(
    gender = "All",
    interruption_proportion = total_interruptions / total_speeches
  )

# Combine data
final_data <- bind_rows(interruptions_by_year_gender, interruptions_by_year_all)

```

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-2
#| fig-cap: "Yearly Interruptions Proportions in Australian Parliament by Gender"

ggplot(final_data, aes(x = year, y = interruption_proportion, color = gender)) +
  geom_line(size = 1.2) +  # Thicker lines for better visibility
  geom_point(size = 2) +  # Larger points to highlight data
  labs(
    title = "Yearly Interruptions Proportions\nin Australian Parliament by Gender",  # Add \n for a line break
    x = "Year",
    y = "Total Interruptions Proportions",
    color = "Gender"
  ) +
  scale_color_brewer(palette = "Set2") +  # Use a colorblind-friendly palette
  theme_minimal(base_size = 14) +  # Adjust base font size for readability
  theme(
    legend.position = "top",  # Move legend to the top
    legend.title = element_text(size = 10, face = "bold"),  # Bold legend title
    legend.text = element_text(size = 8),  # Adjust legend text size
    plot.title = element_text(size = 14, face = "bold", hjust = 0.5),  # Center the title
    axis.title = element_text(size = 12),  # Axis title size
    axis.text = element_text(size = 11)  # Axis text size
  ) +
  scale_x_continuous(breaks = seq(min(final_data$year), max(final_data$year), by = 5))  # Adjust x-axis breaks

```

@fig-1 illustrates interruptions in the Australian Parliament from 1998 to 2022, categorized by gender. Notably, male speakers consistently faced more interruptions than females, with a peak in 2011 and a subsequent decline. Female speakers experienced fewer interruptions, with relatively stable figures across the years. The "Unknown" category, consistently low, suggests either minimal occurrence or documentation of such interruptions.

To provide a fair comparison of interruptions across different genders within the Australian Parliament, we normalize the data by calculating proportions. This method addresses the gender imbalance in parliament, ensuring that the analysis reflects the frequency of interruptions relative to each gender's representation. @fig-2 presents the proportions of speeches interrupted by gender. It indicates that male speakers had a higher proportion of their speeches interrupted, especially during the mid-2000s to early 2010s, though the gap between genders has narrowed over time. The proportion of interruptions for female speakers generally mirrors these fluctuations, implying that specific topics or periods may have incited more active parliamentary interactions. The "Unknown" gender shows minimal changes, highlighting its limited data representation. This analysis points out both the consistency and evolution of gender dynamics within parliamentary debates over the years.

```{r}
#| include: false
#| warning: false
#| message: false
# Summarize interruptions by year, party, and gender
interruptions_summary <- hansard_corpus %>%
  group_by(year, party, gender) %>%
  summarise(
    total_interruptions = sum(interject, na.rm = TRUE),
    .groups = 'drop'
  )

```

```{r}
#| include: false
#| warning: false
#| message: false
# Plotting the data as a grouped bar chart
ggplot(interruptions_summary, aes(x = party, y = total_interruptions, fill = gender)) +
  geom_bar(stat = "identity", position = position_dodge()) +  # Use position_dodge() for grouped bars
  labs(
    title = "Interruptions by Gender and Party",
    x = "Party",
    y = "Total Interruptions",
    fill = "Gender"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate x-axis labels for better readability

```

```{r}
#| include: false
#| warning: false
#| message: false
# Filter data for only LP and ALP parties and summarize interruptions by gender
interruptions_major_parties <- hansard_corpus %>%
  filter(party %in% c("LP", "ALP")) %>%
  mutate(
    interject = as.numeric(interject)  # Ensure interject is numeric
  ) %>%
  group_by(party, gender) %>%
  summarise(
    total_interruptions = sum(interject, na.rm = TRUE),
    .groups = 'drop'
  )

```

```{r}
#| include: false
#| warning: false
#| message: false
# Assuming the 'hansard_corpus' and 'interject' are properly loaded and converted
# First, let's create a summary for each gender within the two parties.
interruptions_gender <- hansard_corpus %>%
  filter(party %in% c("LP", "ALP")) %>%
  group_by(party, gender) %>%
  summarise(
    total_interruptions = sum(as.numeric(interject), na.rm = TRUE),
    .groups = 'drop'
  )

```

```{r}
#| include: false
#| warning: false
#| message: false
# Plotting with the inclusion of "All"
ggplot(interruptions_major_parties, aes(x = party, y = total_interruptions, fill = gender)) +
  geom_bar(stat = "identity", position = position_dodge(), width = 0.7) +
  scale_fill_manual(values = c("Female" = "#FF9999", "Male" = "#9999FF")) +  # Color for "All"
  labs(
    title = "Gender-based and Total Interruptions\nin Major Australian Political Parties",
    x = "Political Party",
    y = "Total Interruptions",
    fill = "Gender"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(face = "bold", size = 14, hjust=0.5),
    plot.subtitle = element_text(face = "italic"),
    axis.title = element_text(size = 12),
    axis.text.x = element_text(angle = 0, vjust = 0.5),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 9)
  )

```
```{r}
#| include: false
#| warning: false
#| message: false
# Calculate the normalized proportion (probability of interruption)
interruptions_normalized <- hansard_corpus %>%
  filter(party %in% c("LP", "ALP")) %>%
  group_by(party, gender) %>%
  summarise(
    total_interruptions = sum(as.numeric(interject), na.rm = TRUE),  # Total interruptions by gender and party
    total_speeches = n(),  # Total speeches by gender and party
    .groups = 'drop'
  ) %>%
  mutate(
    interruption_probability = total_interruptions / total_speeches  # Normalized proportion (probability)
  )

```

```{r}
#| include: false
#| warning: false
#| message: false
# Plotting the normalized proportions
ggplot(interruptions_normalized, aes(x = party, y = interruption_probability, fill = gender)) +
  geom_bar(stat = "identity", position = position_dodge(), width = 0.7) +  # Bar plot with proportions
  scale_fill_manual(values = c("Female" = "#FF9999", "Male" = "#9999FF")) +  # Custom colors for gender
  labs(
    title = "Normalized Gender-based Interruptions\nin Major Australian Political Parties",
    x = "Political Party",
    y = "Probability of Interruption",
    fill = "Gender"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(face = "bold", size = 14, hjust = 0.5),
    axis.title = element_text(size = 12),
    axis.text.x = element_text(angle = 0, vjust = 0.5),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 9)
  )

```

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-3
#| fig-cap: "Interruptions in Major Australian Political Parties by Gender"

# Remove the legend from the first plot
plot1 <- ggplot(interruptions_major_parties, aes(x = party, y = total_interruptions, fill = gender)) +
  geom_bar(stat = "identity", position = position_dodge(), width = 0.7) +
  scale_fill_manual(values = c("Female" = "#FF9999", "Male" = "#9999FF")) +  # Colors for genders
  labs(
    x = "Political Party",
    y = "Total Interruptions"
  ) +
  theme_minimal() +
  theme(
    plot.subtitle = element_text(face = "bold", size = 12, hjust = 0.5),  # Subtitle styling
    axis.title = element_text(size = 11),
    axis.text.x = element_text(angle = 0, vjust = 0.5),
    legend.position = "none",  # Remove the legend
    legend.text = element_text(size = 9)
  )

# Keep the legend only in the second plot
plot2 <- ggplot(interruptions_normalized, aes(x = party, y = interruption_probability, fill = gender)) +
  geom_bar(stat = "identity", position = position_dodge(), width = 0.7) +  # Bar plot with proportions
  scale_fill_manual(values = c("Female" = "#FF9999", "Male" = "#9999FF")) +  # Custom colors for gender
  labs(
    x = "Political Party",
    y = "Probability of Interruption",
    fill = "Gender"
  ) +
  theme_minimal() +
  theme(
    plot.subtitle = element_text(face = "bold", size = 12, hjust = 0.5),  # Subtitle styling
    axis.title = element_text(size = 11),
    axis.text.x = element_text(angle = 0, vjust = 0.5),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 9)
  )

# Add a combined title and arrange plots with patchwork
(plot1 + plot2) +
  plot_annotation(
    title = "Interruptions in Major Australian Political Parties by Gender",
    theme = theme(
      plot.title = element_text(size = 12, face = "bold", hjust = 0.5)  # Big title styling
    )
  )

```

@fig-3 focuses on the Liberal Party (LP) and the Australian Labor Party (ALP), the two major parties in Australian politics, to analyze interruptions by gender. Since these parties dominate parliamentary proceedings, they provide a significant sample of gender interaction dynamics. The total interruptions are higher in the ALP compared to the LP, with male members experiencing more interruptions than female members in both parties. We use proportions to normalize the data, accounting for differences in gender representation within these parties. This approach helps us understand the rate at which female and male members are interrupted relative to their participation, offering a clearer insight into the parliamentary discourse dynamics.

# Introduction

Overview paragraph

Estimand paragraph

Results paragraph

Why it matters paragraph

Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....
git config --global http.postBuffer 524288000

git config --global http.postBuffer 629145600

git reset --soft HEAD~1

git lfs install
git lfs track "*.parquet"
git add .gitattributes
git commit -m "Track large parquet files with Git LFS"
git add data/01-raw_data/hansard-corpus/hansard_corpus_1998_to_2022.parquet
git commit -m "Add large Hansard Parquet file"
git push origin main

# Data {#sec-data}

## Overview

## Measurement

Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.

## Outcome variables

Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.

Talk way more about it.

## Predictor variables

Add graphs, tables and text.

Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.

# Model

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

Please don't use these as sub-heading labels - change them to be what your point actually is.

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

## Diagnostics

\newpage

# References

### 2024-12-02 scripts/03-clean_data.R

@@ -1,44 +1,60 @@
 #### Preamble ####
-# Purpose: Cleans the raw plane data recorded by two observers..... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 6 April 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Cleans the raw data 
+# Author: Rohan Alexander Hannah Yu
+# Date: 2 12, 2024
+# Contact: rohan.alexander@utoronto.ca realhannah.yu@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: [02-download_data]
 
 #### Workspace setup ####
 library(tidyverse)
 
 #### Clean data ####
-raw_data <- read_csv("inputs/data/plane_data.csv")
+raw_data <- read_parquet("data/01-raw_data/hansard_corpus_1998_to_2022.parquet")
 
-cleaned_data <-
-  raw_data |>
-  janitor::clean_names() |>
-  select(wing_width_mm, wing_length_mm, flying_time_sec_first_timer) |>
-  filter(wing_width_mm != "caw") |>
+library(dplyr)
+library(tidyr)
+library(lubridate)
+
+
+# Explore the Data
+summary(raw_data)
+str(raw_data)
+
+# Assuming 'raw_data' is already loaded
+
+# Ensure that 'gender' is treated as a character if it's not already, especially if it's a factor
+raw_data <- raw_data %>%
   mutate(
-    flying_time_sec_first_timer = if_else(flying_time_sec_first_timer == "1,35",
-                                   "1.35",
-                                   flying_time_sec_first_timer)
-  ) |>
-  mutate(wing_width_mm = if_else(wing_width_mm == "490",
-                                 "49",
-                                 wing_width_mm)) |>
-  mutate(wing_width_mm = if_else(wing_width_mm == "6",
-                                 "60",
-                                 wing_width_mm)) |>
+    gender = as.character(gender),  # Convert factor to character to handle empty strings correctly
+    gender = if_else(is.na(gender) | gender == "", "Unknown", gender)  # Replace NA and empty strings
+  )
+
+raw_data <- raw_data %>%
   mutate(
-    wing_width_mm = as.numeric(wing_width_mm),
-    wing_length_mm = as.numeric(wing_length_mm),
[…]

### 2025-01-10 paper/paper.qmd
add in.gov, count, etc.

@@
 ---
+
+# Introduction {#sec-introduction}
+
+Although interjections are officially prohibited during a member's speech in the Australian Parliament, interruptions still occur frequently, particularly during heated debates often fueled by political disagreements [@aphInterruptions2025].
+This raises crucial questions about gender dynamics within the context of parliamentary debates in Australia.
+Concerns are growing regarding whether women are disproportionately interrupted compared to men, highlighting potential underlying biases that could influence the effectiveness and fairness of parliamentary proceedings.
+
+There has been considerable research on speech patterns and gender-based interruptions in government speeches across various countries.
+For instance, during U.S.
+Supreme Court confirmation hearings, female and minority nominees are interrupted more frequently than their male and white counterparts [@genderRaceSCCHearings2024].
+Additionally, in the US Congress, women also experienced more interruptions than men, especially during discussions of women’s issues, where women are more than twice as likely to be interrupted compared to non-gendered topics [@genderInterruptionsCongress2022].
+In the Ecuadorian Congress, female legislators not only deliver fewer speeches but also speak for shorter durations compared to their male peers.
+Furthermore, women often wait longer to regain the floor after interruptions, leading them to strategically shorten their speeches to minimize further disruptions.
+However, women in authoritative positions can mitigate some of these interruption-related penalties, with senior women's speeches often exceeding those of men in length when they achieve comparable levels of experience or hold significant roles [@vera2021politics].
+
+Contrastingly, studies of the Australian High Court reveal a different dynamic [@jacobiPredictabilityInterruptions].
+The result suggested that contrary to the U.S.
+Supreme Court, there is no significant difference between female and male justices regarding interruptions.
+Although women experience a higher rate of interruptions relative to their speaking time, the subtlety of this effect suggests that gender dynamics within the Australian court might be more balanced compared to the U.S.
+Supreme Court.
+This highlights the differences in how judicial interactions are influenced by gender across different legal systems.
+
+Building on existing literature suggesting that the Australian High Court may exhibit better gender dynamics than its counterparts in the US, we aim to delve deeper into the issue of gender-based interruptions within the Australian Parliament.
+Utilizing the Australian Hansard, the official written record of parliamentary debates which has been digitized by Lindsay Katz and Rohan Alexander, we have access to comprehensive records of all parliamentary proceedings from 1998 to 2022 [@katz2023digitization].
+From the dataset, we aim to analyze the frequency and context of interruptions based on gender.
+Specifically, our study will focus on comparing the rates at which male and female parliamentarians are interrupted during their speeches.
+
+The remainder of this paper is structured as follows: @sec-data demonstrates the data used for this paper, @sec-model describes, justifies, and explains my model, @sec-results highlights the results of the predictions using tables and graphs, and @sec-discussion contains important implications and conclusions based on the findings.
+
+# Data {#sec-data}
+
+# Model {#sec-model}
+# Results {#sec-results}
 
@@
 library(patchwork)
+library(kableExtra)
+library(dplyr)
+library(stringr)
 
@@
 # View the first few rows
-head(hansard_corpus)
+head(hansard_corpus, 150)
 
@@
 summary(hansard_corpus)
+
 ```
@@
     table.border.bottom.color = "gray"
+  )%>%
+  tab_style(
+    style = cell_text(align = "left"),  # Align text to the left
+    locations = cells_body(columns = everything())  # Apply to all columns in the body
   )
@@
   labs(
-    title = "Yearly Interruptions in Australian Parliament by Gender",
+    title = "Yearly Interruptions in Australian\nParliament by Gender",
     x = "Year",
@@
     legend.text = element_text(size = 8),  # Adjust legend text size
-    plot.title = element_text(size = 14, face = "bold"),  # Bold title
+    plot.title = element_text(size = 14, face = "bold",  hjust = 0.5),  # Bold title
     axis.title = element_text(size = 12),  # Axis title size
@@
 # Combine data
-final_data <- bind_rows(interruptions_by_year_gender, interruptions_by_year_all)
+final_data1 <- bind_rows(interruptions_by_year_gender, interruptions_by_year_all)
 
@@
 
-ggplot(final_data, aes(x = year, y = interruption_proportion, color = gender)) +
+ggplot(final_data1, aes(x = year, y = interruption_proportion, color = gender)) +
   geom_line(size = 1.2) +  # Thicker lines for better visibility
@@
 This analysis points out both the consistency and evolution of gender dynamics within parliamentary debates over the years.
+
+```{r}
+#| include: false
+#| warning: false
+#| message: false
+print(final_data1)
+
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| label: fig-2_chamber
+#| fig-cap: "Yearly Interruptions Proportions in Australian Parliament by Gender (Chamber)"
+
+no_fedchamb <- hansard_corpus %>%
+  filter(fedchamb_flag == 0)
+
+# Group by year and gender to summarize interruptions
+interruptions_by_year_gender <- no_fedchamb %>%
+  group_by(year, gender) %>%
+  summarise(
+    total_interruptions = sum(interject, na.rm = TRUE),
+    total_speeches = n(),
+    .groups = 'drop'
+  ) %>%
+  mutate(
+    interruption_proportion = total_interruptions / total_speeches
+  )
+
+# Calculate interruptions for all genders combined per year
+interruptions_by_year_all <- no_fedchamb %>%
+  group_by(year) %>%
+  summarise(
+    total_interruptions = sum(interject, na.rm = TRUE),
+    total_speeches = n(),
+    .groups = 'drop'
+  ) %>%
+  mutate(
+    gender = "All",
+    interruption_proportion = total_interruptions / total_speeches
+  )
+
+# Combine the gender-specific and overall data
+final_data2 <- bind_rows(interruptions_by_year_gender, interruptions_by_year_all)
+
+# Plotting the interruptions proportions by year and gender
+ggplot(final_data2, aes(x = year, y = interruption_proportion, color = gender)) +
+  geom_line(size = 1.2) +  # Use thicker lines for better visibility
+  geom_point(size = 2) +  # Use larger points to highlight data points
+  labs(
+    title = "Yearly Interruptions Proportions\nin Australian Parliament by Gender (Chamber)",
+    x = "Year",
+    y = "Total Interruptions Proportions",
+    color = "Gender"
+  ) +
+  scale_color_brewer(palette = "Set2") +  # Use a colorblind-friendly palette
+  theme_minimal(base_size = 14) +  # Use a minimal theme with readable base font size
+  theme(
+    legend.position = "top",  # Position legend at the top for better accessibility
+    legend.title = element_text(size = 10, face = "bold"),  # Bold the legend title
+    legend.text = element_text(size = 8),  # Set legend text size
+    plot.title = element_text(size = 14, face = "bold", hjust = 0.5),  # Center and bold the plot title
+    axis.title = element_text(size = 12),  # Set axis title size
+    axis.text = element_text(size = 11)  # Set axis text size
+  ) +
+  scale_x_continuous(breaks = seq(min(final_data$year), max(final_data$year), by = 5))  # Set x-axis breaks every 5 years
+
+```
+```{r}
+#| include: false
+#| warning: false
+#| message: false
+# Displaying the table of final data
+print(final_data2)
+
+```
+
+```{r}
+#| include: false
+#| warning: false
+#| message: false
+# Pivot to get male and female data on the same row
+comparison_data <- final_data2 %>%
+  pivot_wider(
+    id_cols = year,
+    names_from = gender,
+    values_from = interruption_proportion
+  )
+
+# Determine which gender had more interruptions per year
+yearly_comparison <- comparison_data %>%
+  mutate(
+    More_Interrupted_Gender = case_when(
+      Male > Female ~ "Male",
+      Female > Male ~ "Female",
+      TRUE ~ "Equal"
+    )
+  )
+
+# Count the number of years each gender was interrupted more
+gender_counts <- yearly_comparison %>%
+  count(More_Interrupted_Gender)
+
+```
+
+```{r}
+#| include: false
+#| warning: false
+#| message: false
+# Determine which gender had more interruptions per year
+yearly_comparison <- comparison_data %>%
+  mutate(
+    More_Interrupted_Gender = case_when(
+      Male > Female ~ "Male",
+      Female > Male ~ "Female",
+      TRUE ~ "Equal"  # This handles cases where the interruption proportions are the same
+    )
+  ) %>%
+  select(year, More_Interrupted_Gender)  # Select only the year and the more interrupted gender columns
+
+# Print the simplified table
+print(yearly_comparison)
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| tbl-cap: "Gender Interruption Proportions Annual Comparison Across General and Chamber"
+#| label: tbl-compareyear
+# Prepare the data
+comparison_all <- final_data1 %>%
+  pivot_wider(
+    id_cols = year,
+    names_from = gender,
+    values_from = interruption_proportion
+  ) %>%
+  mutate(
+    More_Interrupted_Gender_All = case_when(
+      Male > Female ~ "Male",
+      Female > Male ~ "Female",
+      TRUE ~ "Equal"
+    )
+  )
+
+comparison_chamber <- final_data2 %>%
+  pivot_wider(
+    id_cols = year,
+    names_from = gender,
+    values_from = interruption_proportion
+  ) %>%
+  mutate(
+    More_Interrupted_Gender_Chamber = case_when(
+      Male > Female ~ "Male",
+      Female > Male ~ "Female",
+      TRUE ~ "Equal"
+    )
+  )
+
+# Assuming final_comparison is prepared as follows
+final_comparison <- comparison_all %>%
+  select(year, More_Interrupted_Gender_All) %>%
+  left_join(comparison_chamber %>% select(year, More_Interrupted_Gender_Chamber), by = "year")
+
+final_comparison %>%
+  gt %>%
+  cols_label(
+    year = "Year",
+    More_Interrupted_Gender_All = "More Interrupted Gender All",
+    More_Interrupted_Gender_Chamber = "More Interrupted Gender Chamber")%>%
+  tab_style(
+    style = cell_text(align = "left"),  # Align text to the left
+    locations = cells_body(columns = everything())  # Apply to all columns in the body
+  )
+
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| label: fig-compare
+#| fig-cap: "Yearly Interruptions Proportions in Australian Parliament by Gender"
+
+# Original dataset, no condition on fedchamb_flag
+interruptions_original <- hansard_corpus %>%
+  filter(gender %in% c("Male", "Female")) %>%
+  mutate(
+    date = as.Date(date, format = "%Y-%m-%d"),
+    year = if_else(is.na(date), NA_integer_, year(date))
+  ) %>%
+  group_by(year, gender) %>%
+  summarise(
+    total_interruptions = sum(interject, na.rm = TRUE),
+    total_speeches = n(),
+    .groups = 'drop'
+  ) %>%
+  mutate(
+    interruption_proportion = total_interruptions / total_speeches,
+    condition = "All Data"
+  )
+
+# Dataset with fedchamb_flag == 0
+interruptions_fedchamb_flag_0 <- hansard_corpus %>%
+  filter(gender %in% c("Male", "Female"), fedchamb_flag == 0) %>%
+  mutate(
+    date = as.Date(date, format = "%Y-%m-%d"),
+    year = if_else(is.na(date), NA_integer_, year(date))
+  ) %>%
+  group_by(year, gender) %>%
+  summarise(
+    total_interruptions = sum(interject, na.rm = TRUE),
+    total_speeches = n(),
+    .groups = 'drop'
+  ) %>%
+  mutate(
+    interruption_proportion = total_interruptions / total_speeches,
+    condition = "fedchamb_flag = 0"
+  )
+
+# Combine the datasets
+final_data3 <- bind_rows(interruptions_original, interruptions_fedchamb_flag_0)
+
+# Adjust labels for condition and linetype
+ggplot(final_data3, aes(x = year, y = interruption_proportion, color = gender, linetype = condition)) +
+  geom_line(size = 1.2) +
+  geom_point(size = 2) +
+  labs(
+    title = "Yearly Interruptions Proportions in\nAustralian Parliament by Gender",
+    subtitle = "Comparing All Data vs. Chamber Data Only",
+    x = "Year",
+    y = "Interruption Proportion",
+    color = "Gender",
+    linetype = "Dataset Type"
+  ) +
+  scale_color_brewer(palette = "Set2") +
+  scale_linetype_manual(values = c("solid", "dotted"), 
+                        labels = c("All", "Chamber")) +
+  theme_minimal(base_size = 14) +
+  theme(
+    legend.position = "top",
+    legend.title = element_text(size = 10, face = "bold"),
+    legend.text = element_text(size = 8),
+    plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
+    plot.subtitle = element_text(size = 12, face = "italic", hjust = 0.5),
+    axis.title = element_text(size = 12),
+    axis.text = element_text(size = 11)
+  ) +
+  scale_x_continuous(breaks = seq(min(final_data3$year), max(final_data3$year), by = 5))  # Adjust x-axis breaks
+
+```
+
+Only analyzing Chamber members, @fig-2_chamber again illustrates interruptions in the Australian Parliament from 1998 to 2022, categorized by gender.
+To distinguish the differences across the two figures, @fig-compare contains both the interruptions for all data and Chamber member data.
+While the interruption patterns in the chamber-only data in @fig-2_chamber largely mirror those observed in the comprehensive dataset @fig-2, there are slight increases in the interruption proportions for women, indicating a potentially heightened level of disruption experienced by female members in non-federal chambers.
+
+@tbl-compareyear displays the more interrupted gender every year in the parliament and compares all members and only chamber members.
+While most years are the same, there is a notable shift in the gender experiencing more frequent interruptions from 2018 to 2020.
+In the broader dataset, males were more frequently interrupted; however, this pattern shifts in the non-federal chamber data, where females became the more interrupted gender during these years.
+This change highlights the variability in gender dynamics within different parliamentary environments and suggests that factors specific to non-federal chamber settings may influence these interaction patterns more significantly for female members.
+
+```{r}
+#| include: false
+#| warning: false
+#| message: false
+# Filter and aggregate data based on the 'question' flag and 'gender'
+interruptions_question_analysis <- hansard_corpus %>%
+  filter(gender %in% c("Male", "Female")) %>%
+  group_by(gender, is_question = as.factor(question)) %>%
+  summarise(
+    total_interruptions = sum(interject, na.rm = TRUE),
+    total_speeches = n(),
+    total_speeches = sum(total_speeches),
+    interruption_proportion = total_interruptions / total_speeches,
+    .groups = 'drop'
+  )
+
+# Print the resulting dataset to verify
+print(interruptions_question_analysis)
+
+```
+
+```{r}
+#| include: false
+#| warning: false
+#| message: false
+# Filter and aggregate data based on the 'question' flag and 'gender'
+interruptions_question_analysis <- hansard_corpus %>%
+  filter(gender %in% c("Male", "Female")) %>%
+  group_by(gender, is_answer = as.factor(answer)) %>%
+  summarise(
+    total_interruptions = sum(interject, na.rm = TRUE),
+    total_speeches = n(),
+    total_speeches = sum(total_speeches),
+    interruption_proportion = total_interruptions / total_speeches,
+    .groups = 'drop'
+  )
+
+# Print the resulting dataset to verify
+print(interruptions_question_analysis)
+```
 
@@
 ```
+
 ```{r}
@@
 
+```{r}
+#| include: false
+#| warning: false
+#| message: false
+# Calculate basic summary statistics for in.gov
+in_gov_stats <- hansard_corpus %>%
+  summarise(
+    Count_In_Gov = sum(in.gov == 1, na.rm = TRUE),
+    Count_Not_In_Gov = sum(in.gov == 0, na.rm = TRUE),
+    Count_NA = sum(is.na(in.gov)),
+    Total = n()
+  )
+
+print(in_gov_stats)
+
+```
+
+```{r}
+#| include: false
+#| warning: false
+#| message: false
+# Calculate basic summary statistics for in.gov
+interject_stats <- hansard_corpus %>%
+  summarise(
+    Count_Interject = sum(interject == 1, na.rm = TRUE),
+    Count_No_Interject = sum(interject == 0, na.rm = TRUE),
+    Count_NA = sum(is.na(interject)),
+    Total = n()
+  )
+
+print(interject_stats)
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| tbl-cap: "Interruption Summary by Government Status (All)"
+#| label: tbl-ingov1
+
+# Assume that interruption_summary is already prepared as previously coded
+interruption_summary <- hansard_corpus %>%
+  mutate(
+    in_gov = factor(in.gov, levels = c(0, 1), labels = c("In Opposition", "In Government")),
+    interject = factor(interject, levels = c(0, 1), labels = c("No", "Yes"))
+  ) %>%
+  group_by(in_gov, interject) %>%
+  summarise(
+    Count = n(),
+    .groups = 'drop'
+  ) %>%
+  arrange(in_gov, desc(interject)) %>%
+  rename(
+    `Government Status` = in_gov,
+    `Interruption` = interject,
+    `Count` = Count
+  )
+
+# Create a clean and professional table
+interruption_summary %>%
+  gt() %>%
+  tab_style(
+    style = cell_text(align = "left"),  # Align text to the left
+    locations = cells_body(columns = everything())  # Apply to all columns in the body
+  )
+
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| tbl-cap: "Interruption Summary by Government Status in Non-Federal Chamber Sessions"
+#| label: tbl-ingov2
+
+# Assume that interruption_summary is already prepared as previously coded
+interruption_summary <- hansard_corpus %>%
+  filter(fedchamb_flag == 0) %>%
+  mutate(
+    in_gov = factor(in.gov, levels = c(0, 1), labels = c("In Opposition", "In Government")),
+    interject = factor(interject, levels = c(0, 1), labels = c("No", "Yes"))
+  ) %>%
+  group_by(in_gov, interject) %>%
+  summarise(
+    Count = n(),
+    .groups = 'drop'
+  ) %>%
+  arrange(in_gov, desc(interject)) %>%
+  rename(
+    `Government Status` = in_gov,
+    `Interruption` = interject,
+    `Count` = Count
+  )
+interruption_summary %>%
+  gt() %>%
+  tab_style(
+    style = cell_text(align = "left"),  # Align text to the left
+    locations = cells_body(columns = everything())  # Apply to all columns in the body
+  )
+
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| label: fig-gov
+#| fig-cap: "Count of Interruptions by Government Status and Gender"
+
+# Prepare the data with absolute counts
+interruption_counts <- hansard_corpus %>%
+  filter(gender %in% c("Male", "Female")) %>%
+  filter(fedchamb_flag == 0) %>%
+  mutate(
+    in_gov = factor(ifelse(is.na(in.gov), "NA", ifelse(in.gov == 1, "In Government", "In Opposition")),
+                    levels = c("In Opposition", "In Government", "NA")),
+    interject = factor(interject, levels = c(0, 1), labels = c("No", "Yes"))
+  ) %>%
+  group_by(in_gov, interject, gender) %>%
+  summarise(
+    Count = n(),
+    .groups = 'drop'
+  )
+
+# Plot using ggplot2 with updated colors and adjusted x-axis labels
+ggplot(interruption_counts, aes(x = in_gov, y = Count, fill = interject)) +
+  geom_bar(stat = "identity", position = "stack") +
+  facet_wrap(~ gender, scales = "free_y") +
+  labs(
+    title = "Interruptions Count by Government Status and Gender",
+    x = "Government Status",
+    y = "Count of Interruptions",
+    fill = "Interruption Occurred"
+  ) +
+  scale_fill_manual(values = c("No" = "steelblue", "Yes" = "salmon")) +
+  theme_minimal() +
+  theme(
+    axis.text.x = element_text(angle = 0, vjust = 2, hjust = 0.5), # Adjust label positioning
+    plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
+    legend.position = "bottom"
+  )
+
+```
+
+@tbl-ingov1, @tbl-ingov2, and @fig-gov offer a detailed look at interruptions during parliamentary sessions, categorized by members' government status and gender.
+Notably, interruptions are extremely rare for members with clearly identified status.
+This indicates a potential correlation between established government status and more orderly interactions, highlighting the importance of role clarity in maintaining decorum.
+
+However, the significant amount of missing data makes reliable inferences about the true nature of interruptions and their correlation with member status challenging.
+The vast majority of interruptions occur when the government status of the speaker is unknown.
+This trend is consistent across both the comprehensive dataset and the subset limited to non-federal chamber sessions.
+Interruptions are exceedingly rare for members whose government status is known, with only 22 interruptions for those "In Government" and an even fewer 4 for those "In Opposition" across all data.
+Due to this substantial amount of missing information, it is very difficult to firmly conclude whether our observed patterns hold true.
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| tbl-cap: "Summary of Parliamentary Session Activities and Interruptions"
+#| label: tbl-qa_interrupt1
+# Assuming hansard_corpus is already loaded and prepped
+summary_stats <- hansard_corpus %>%
+  mutate(
+    question_numeric = as.numeric(as.character(question)),
+    answer_numeric = as.numeric(as.character(answer))
+  ) %>%
+  summarise(
+    Questions = sum(question_numeric, na.rm = TRUE),
+    Answers = sum(answer_numeric, na.rm = TRUE),
+    Total_Interruptions = sum(interject, na.rm = TRUE),
+    Interruptions_During_Questions = sum(interject[question_numeric == 1], na.rm = TRUE),
+    Interruptions_During_Answers = sum(interject[answer_numeric == 1], na.rm = TRUE)
+  )
+
+summary_stats %>%
+  gt() %>%
+  cols_label(
+    Questions = "Questions",
+    Answers = "Answers",
+    Total_Interruptions = "Total Interruptions",
+    Interruptions_During_Questions = "Question Interrupted",
+    Interruptions_During_Answers = "Answer Interrupted"
+  ) %>%
+  tab_style(
+    style = cell_text(align = "left"),
+    locations = cells_body(columns = everything())
+  ) %>%
+  tab_options(
+    table.width = pct(100),  # Set the table width to 100% of the container
+    table.align = "left"  # Align the table to the left of the container
+  ) %>%
+  tab_style(
+    style = cell_text(align = "left"),  # Align text to the left
+    locations = cells_body(columns = everything())  # Apply to all columns in the body
+  )
+
+```
+
+```{r}
+#| include: false
+#| warning: false
+#| message: false
+# Review entries where questions or answers are marked
+question_instances <- hansard_corpus %>%
+  filter(question == 1)
+print(question_instances)
+```
+
+```{r}
+#| include: false
+#| warning: false
+#| message: false
+# Filter and aggregate data based on the 'question' flag and 'gender'
+interruptions_question_analysis <- hansard_corpus %>%
+  filter(gender %in% c("Male", "Female")) %>%
+  group_by(gender, is_question = as.factor(question)) %>%
+  summarise(
+    total_interruptions = sum(interject, na.rm = TRUE),
+    total_speeches = n(),
+    total_speeches = sum(total_speeches),
+    interruption_proportion = total_interruptions / total_speeches,
+    .groups = 'drop'
+  )
+
+# Print the resulting dataset to verify
+print(interruptions_question_analysis)
+
+```
+
+```{r}
+#| include: false
+#| warning: false
+#| message: false
+# Filter and aggregate data based on the 'question' flag and 'gender'
+interruptions_question_analysis <- hansard_corpus %>%
+  filter(gender %in% c("Male", "Female")) %>%
+  group_by(gender, is_answer = as.factor(answer)) %>%
+  summarise(
+    total_interruptions = sum(interject, na.rm = TRUE),
+    total_speeches = n(),
+    total_speeches = sum(total_speeches),
+    interruption_proportion = total_interruptions / total_speeches,
+    .groups = 'drop'
+  )
+
+# Print the resulting dataset to verify
+print(interruptions_question_analysis)
+```
+
+```{r}
+#| include: false
+#| warning: false
+#| message: false
+# Assuming your dataset is named 'hansard_corpus'
+# Calculate the word count for each 'body' entry
+hansard_corpus1 <- hansard_corpus %>%
+  mutate(word_count = str_count(body, "\\b\\w+\\b"))
+
+# Print the data to see the word counts
+head(hansard_corpus1)
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| label: fig-gov3
+#| fig-cap: "Histogram of Word Counts in Speeches (Up to 250 Words)"
+
+hansard_corpus1 <- hansard_corpus1 %>%
+  filter(gender %in% fedchamb_flag == 0)
+
+# Enhanced histogram with interjection data
+ggplot(hansard_corpus1 %>% filter(word_count <= 250), aes(x = word_count, fill = as.factor(interject))) +
+  geom_histogram(binwidth = 25, position = "identity", alpha = 0.6) +
+  labs(
+    title = "Histogram of Word Counts in Speeches (Up to 250 Words)",
+    x = "Word Count",
+    y = "Frequency",
+    fill = "Interjection Occurred"
+  ) +
+  scale_fill_manual(values = c("0" = "steelblue", "1" = "salmon"), labels = c("No", "Yes")) +
+  theme_minimal() +
+  theme(legend.position = "top") +
+  theme(
+   plot.title = element_text(size = 14, face = "bold", hjust = 0.5))
+```
+@fig-gov3 shows word counts in speeches divided into two categories: speeches where an interjection occurred and those without any interruptions.
+We can see that speeches without interruptions (blue bars) are more frequent across all word count ranges, especially as the number of words increases.
+Conversely, interrupted speeches (red bars) are less frequent and generally shorter.
+This trend suggests that interruptions tend to happen in shorter speeches or possibly cause speakers to shorten their remarks.
+This graph gives a clear visual indication of how interruptions might disrupt or influence the length of parliamentary speeches.
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| label: tbl-gov4
+#| tbl-cap: "Gender-Based Interruptions and Word Count"
+# Assuming hansard_corpus1 is already loaded and prepared
+# First, filter to include only speeches up to 1000 words and only Male or Female
+filtered_data <- hansard_corpus1 %>%
+  filter(gender %in% c("Male", "Female"))
+
+# Group by gender and whether there was an interjection
+summary_table <- filtered_data %>%
+  group_by(gender, interject) %>%
+  summarise(
+    num_speeches = n(),
+    average_words = mean(word_count, na.rm = TRUE),
+    min_words = min(word_count, na.rm = TRUE),
+    max_words = max(word_count, na.rm = TRUE),
+    .groups = 'drop'
+  )
+
+summary_table %>%
+  gt()%>%
+  tab_style(
+    style = cell_text(align = "left"),  # Align text to the left
+    locations = cells_body(columns = everything())  # Apply to all columns in the body
+  ) %>%
+  cols_label(
+    gender = "Gender",
+    interject = "Interruption",
+    num_speeches = "Total Speeches",
+    average_words = "Average Words",
+    min_words = "Min Words",
+    max_words = "Max Words")
+
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| label: fig-gov5
+#| fig-cap: "Gender-Based Interruptions and Word Count"
+# Bar plot for total speeches with real numbers on the y-axis
+ggplot(summary_table, aes(x = gender, y = num_speeches, fill = factor(interject))) +
+  geom_bar(stat = "identity", position = "dodge") +
+  scale_fill_manual(values = c("steelblue", "salmon"), labels = c("No", "Yes")) +
+  scale_y_continuous(labels = scales::comma) +  # Display real numbers on the y-axis
+  labs(
+    title = "Total Speeches by Gender and Interruption",
+    x = "Gender",
+    y = "Total Speeches",
+    fill = "Interruption"
+  ) +
+  theme_minimal(base_size = 14) +
+  theme(
+    legend.position = "top",
+    plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
+    axis.title = element_text(size = 12),
+    axis.text = element_text(size = 10)
+  )
+
+```
+@tbl-gov4 and @fig-gov5 highlights that, on average, females tend to speak longer than males before an interruption occurs.
+For uninterrupted speeches, females average 560.72 words compared to 448.67 words for males.
+Even when interrupted, female speeches still have a higher average word count (37.76 words) than interrupted male speeches (28.76 words).
+This suggests that while females may face greater challenges overall, they tend to hold the floor longer before interruptions occur.
+However, the substantial drop in average word count for both genders during interruptions shows the disruptive impact, with females experiencing a steeper decline relative to their uninterrupted averages.
+This pattern indicates that while females often manage to speak at greater length initially, interruptions disproportionately diminish their overall speaking opportunities.
+
+# Discussion {#sec-discussion}
+
 # Introduction
@@
 git push origin main
-
-# Data {#sec-data}
 

### 2025-01-15 paper/paper.qmd
edit the scripts

@@
 ---
-title: "Voices in Parliament: Analyzing Interruptions Across Gender in the Australian Political Landscape"
+title: "Gender Dynamics of Parliamentary Interruptions: A Detailed Analysis of Speech Disruptions in the Australian Parliament (1998-2022)"
 subtitle: "My subtitle if needed"
@@
 ```{r}
-#| include: false
 #| warning: false
@@
   theme(
-    axis.text.x = element_text(angle = 0, vjust = 2, hjust = 0.5), # Adjust label positioning
+    axis.text.x = element_text(size = 7, angle = 0, vjust = 2, hjust = 0.5), # Adjust label positioning
     plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
@@
   labs(
-    title = "Histogram of Word Counts in Speeches (Up to 250 Words)",
+    title = "Histogram of Word Counts in Speeches",
     x = "Word Count",
@@
 # Bar plot for total speeches with real numbers on the y-axis
-ggplot(summary_table, aes(x = gender, y = num_speeches, fill = factor(interject))) +
+ggplot(summary_table, aes(x = gender, y = average_words, fill = factor(interject))) +
   geom_bar(stat = "identity", position = "dodge") +
@@
   labs(
-    title = "Total Speeches by Gender and Interruption",
+    title = "Gender-Based Interruptions and Word Count",
     x = "Gender",

### 2025-01-15 scripts/00-simulate_data.R

@@ -1,52 +1,34 @@
 #### Preamble ####
-# Purpose: Simulates a dataset of Australian electoral divisions, including the 
-  #state and party that won each division.
-# Author: Rohan Alexander
-# Date: 26 September 2024
-# Contact: rohan.alexander@utoronto.ca
+# Purpose: Simulates a dataset of Australian parliament speakers' speeches. 
+# Author: Hannah Yu
+# Date: 13 January 2025
+# Contact: realhannah.yu@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: The `tidyverse` package must be installed
 # Any other information needed? Make sure you are in the `starter_folder` rproj
 
-
 #### Workspace setup ####
 library(tidyverse)
+library(dplyr)
 set.seed(853)
 
 
 #### Simulate data ####
-# State names
-states <- c(
-  "New South Wales",
-  "Victoria",
-  "Queensland",
-  "South Australia",
-  "Western Australia",
-  "Tasmania",
-  "Northern Territory",
-  "Australian Capital Territory"
+# Create a simulated dataset
+data <- tibble(
+  speaker_id = 1:100,  # Speaker numbers from 1 to 100
+  interject = rbinom(100, 1, 0.3),  # Dummy variable for interjection (30% probability)
+  gender = sample(c("Male", "Female"), 100, replace = TRUE),  # Randomly assign gender
+  chamber = sample(c("House of Representatives", "Federation Chamber"), 100, replace = TRUE),  # Randomly assign chamber
+  first_speech = rbinom(100, 1, 0.2),  # Dummy for first speech (20% probability)
+  date = sample(seq(as.Date('1998-01-01'), as.Date('2022-12-31'), by="day"), 100, replace = TRUE),  # Random dates between 1998 and 2022
+  party = sample(c("ALP", "LP", "Nats", "NP", "Other"), 100, replace = TRUE),  # Randomly assign party
+  year = sample(1998:2022, 100, replace = TRUE)  # Randomly assign year from 1998 to 2022
 )
-
-# Political parties
-parties <- c("Labor", "Liberal", "Greens", "National", "Other")
-
-# Create a dataset by randomly assigning states and parties to divisions
-analysis_data <- tibble(
-  division = paste("Division", 1:151),  # Add "Division" to make it a character
-  state = sample(
-    states,
-    size = 151,
-    replace = TRUE,
[…]

### 2025-01-15 scripts/01-test_simulated_data.R

@@ -1,9 +1,9 @@
 #### Preamble ####
 # Purpose: Tests the structure and validity of the simulated Australian 
   #electoral divisions dataset.
-# Author: Rohan Alexander
-# Date: 26 September 2024
-# Contact: rohan.alexander@utoronto.ca
+# Author: Hannah Yu
+# Date: 14 January 2025
+# Contact: realhannah.yu@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: 
   # - The `tidyverse` package must be installed and loaded
@@ -14,6 +14,8 @@
 #### Workspace setup ####
 library(tidyverse)
 
+
+#### Load data for testing ####
 analysis_data <- read_csv("data/00-simulated_data/simulated_data.csv")
 
 # Test if the data was successfully loaded
@@ -23,60 +25,32 @@ if (exists("analysis_data")) {
   stop("Test Failed: The dataset could not be loaded.")
 }
 
-
-#### Test data ####
-
-# Check if the dataset has 151 rows
-if (nrow(analysis_data) == 151) {
-  message("Test Passed: The dataset has 151 rows.")
+# Check if the dataset has 100 rows
+if (nrow(analysis_data) == 100) {
+  message("Test Passed: The dataset has 100 rows.")
 } else {
-  stop("Test Failed: The dataset does not have 151 rows.")
+  stop("Test Failed: The dataset does not have 100 rows.")
 }
 
-# Check if the dataset has 3 columns
-if (ncol(analysis_data) == 3) {
-  message("Test Passed: The dataset has 3 columns.")
+# Check if the dataset has 8 columns
+if (ncol(analysis_data) == 8) {
+  message("Test Passed: The dataset has 8 columns.")
 } else {
-  stop("Test Failed: The dataset does not have 3 columns.")
+  stop("Test Failed: The dataset does not have 8 columns.")
 }
 
-# Check if all values in the 'division' column are unique
-if (n_distinct(analysis_data$division) == nrow(analysis_data)) {
-  message("Test Passed: All values in 'division' are unique.")
-} else {
-  stop("Test Failed: The 'division' column contains duplicate values.")
-}
+# Since there's no 'division' or 'state' column in your dataset, we'll skip those tests
 
-# Check if the 'state' column contains only valid Australian state names
-valid_states <- c("New South Wales", "Victoria", "Queensland", "South Australia", 
-                  "Western Australia", "Tasmania", "Northern Territory", 
[…]

### 2025-01-15 scripts/02-download_data.R

@@ -1,26 +1,46 @@
 #### Preamble ####
-# Purpose: Downloads and saves the data from [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Downloads and saves the data from Zenodo
+# Author: Hannah Yu, Rohan Alexander
+# Date: 11 November 2024
+# Contact: realhannah.yu@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
 
 
 #### Workspace setup ####
-library(opendatatoronto)
 library(tidyverse)
-# [...UPDATE THIS...]
+library(arrow)  # For handling Parquet files
 
 #### Download data ####
-# [...ADD CODE HERE TO DOWNLOAD...]
+
+
+# Install and load necessary package
+if (!require("curl")) install.packages("curl")
+library(curl)
+
+# URL of the data file
+url <- "https://zenodo.org/records/8121950/files/hansard-corpus.zip?download=1"
+
+# Define the destination file name
+destfile <- "data/01-raw_data/Hansard_Corpus_1998_to_2022.zip"
+
+# Set options for a longer timeout (e.g., 10 minutes)
+options(timeout = 3000) 
+
+# Use curl_download for more robust handling of large files
+curl_download(url, destfile)
+
+# Check if the file has been downloaded and then unzip
+if (file.exists(destfile)) {
+  unzip(destfile)
+  # Assuming the unzip contains files in a format to be converted to parquet
+  # You would need additional steps here if your data needs processing before saving it as parquet
+  # Assuming 'the_raw_data' is a dataframe loaded from the unzipped files
+  write_parquet(hansard_corpus, "data/01-raw_data/hansard_corpus.parquet") 
+} else {
+  message("File download failed, please check the URL or network settings.")
+}
 
 
 
-#### Save data ####
-# [...UPDATE THIS...]
-# change the_raw_data to whatever name you assigned when you downloaded it.
-write_csv(the_raw_data, "inputs/data/raw_data.csv") 
 
-         
+

### 2025-01-15 scripts/03-clean_data.R

@@ -1,34 +1,38 @@
 #### Preamble ####
 # Purpose: Cleans the raw data 
 # Author: Rohan Alexander Hannah Yu
-# Date: 2 12, 2024
-# Contact: rohan.alexander@utoronto.ca realhannah.yu@mail.utoronto.ca
+# Date: 2 October, 2024
+# Contact: rohan.alexander@utoronto.ca, realhannah.yu@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: [02-download_data]
 
 #### Workspace setup ####
 library(tidyverse)
-
-#### Clean data ####
-raw_data <- read_parquet("data/01-raw_data/hansard_corpus_1998_to_2022.parquet")
-
 library(dplyr)
 library(tidyr)
 library(lubridate)
+#### Clean data ####
+raw_data <- read_parquet("data/01-raw_data/hansard_corpus.parquet")
+head(raw_data, 150)
 
 
 # Explore the Data
 summary(raw_data)
 str(raw_data)
 
-# Assuming 'raw_data' is already loaded
 
-# Ensure that 'gender' is treated as a character if it's not already, especially if it's a factor
 raw_data <- raw_data %>%
   mutate(
-    gender = as.character(gender),  # Convert factor to character to handle empty strings correctly
-    gender = if_else(is.na(gender) | gender == "", "Unknown", gender)  # Replace NA and empty strings
+    gender = as.character(gender),  # Ensure it's a character
+    gender = if_else(is.na(gender) | gender == "", "Unknown", gender),  # Replace NA and empty strings with "Unknown"
+    gender = case_when(  # Capitalize the values
+      str_to_lower(gender) == "male" ~ "Male",
+      str_to_lower(gender) == "female" ~ "Female",
+      str_to_lower(gender) == "unknown" ~ "Unknown",
+      TRUE ~ gender  # Retain other values if present
+    )
   )
+
 
 raw_data <- raw_data %>%
   mutate(
@@ -40,7 +44,6 @@ raw_data <- raw_data %>%
 
 
 # Correct Data Types
-# Convert interject from factor/character to numeric if it's not already
 raw_data <- raw_data %>%
   mutate(
     interject = as.numeric(interject),
@@ -51,7 +54,6 @@ hansard_corpus$question <- as.numeric(as.character(hansard_corpus$question))
 
 
 # Error Checks
-# Example: Check for any anomalous entries in 'gender' or other crucial fields
 table(raw_data$gender)  # Should only contain known categories
 
 

### 2025-01-15 scripts/04-test_analysis_data.R

@@ -1,69 +1,64 @@
 #### Preamble ####
-# Purpose: Tests... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 26 September 2024 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Tests the analysis data
+# Author: Rohan Alexander, Hannah Yu
+# Date: 14 January 2025
+# Contact: rohan.alexander@utoronto.ca, realhannah.yu@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: 
+  # - 00-simulate_data.R must have been run
+  # - 01-test_simulated.R must have been run
+  # - 02-download_data.R must have been run
+  # - 03-clean_data.R must have been run
 
 
 #### Workspace setup ####
-library(tidyverse)
 library(testthat)
+library(dplyr)
+library(readr)
+library(lubridate)
+library(arrow)
 
-data <- read_csv("data/02-analysis_data/analysis_data.csv")
 
+# Load the cleaned data
+analysis_data <- read_parquet("data/02-analysis_data/cleaned_data.parquet")
 
-#### Test data ####
-# Test that the dataset has 151 rows - there are 151 divisions in Australia
-test_that("dataset has 151 rows", {
-  expect_equal(nrow(analysis_data), 151)
+### Define Tests Using testthat ###
+
+# Test for expected number of rows and columns
+test_that("dataset has the expected number of rows and columns", {
+  expect_true(nrow(analysis_data) > 0)
+  expect_true(ncol(analysis_data) >= 5)  # Adjust based on your actual dataset structure
 })
 
-# Test that the dataset has 3 columns
-test_that("dataset has 3 columns", {
-  expect_equal(ncol(analysis_data), 3)
+# Test for valid gender categories
+test_that("gender column contains only valid categories", {
+  valid_genders <- c("Male", "Female", "Unknown")
+  expect_setequal(unique(analysis_data$gender), valid_genders)
 })
 
-# Test that the 'division' column is character type
-test_that("'division' is character", {
-  expect_type(analysis_data$division, "character")
+
+# Test for all dates being valid and no future dates
+test_that("all dates are valid and no future dates are present", {
+  expect_true(all(analysis_data$date <= Sys.Date()))
 })
 
[…]

### 2025-01-15 scripts/05-model_data.R

@@ -1,0 +1,66 @@
+#### Preamble ####
+# Purpose: Models... [...UPDATE THIS...]
+# Author: Rohan Alexander, Hannah Yu
+# Date: 14 January 2025
+# Contact: rohan.alexander@utoronto.ca, realhannah.yu@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: 
+# - 02-download_data.R must have been run
+# - 03-clean_data.R must have been run
+
+
+
+#### Workspace setup ####
+library(tidyverse)
+library(rstanarm)
+
+#### Read data ####s
+analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
+
+### Model data ####
+first_model <-
+  stan_glm(
+    formula = flying_time ~ length + width,
+    data = analysis_data,
+    family = gaussian(),
+    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
+    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
+    prior_aux = exponential(rate = 1, autoscale = TRUE),
+    seed = 853
+  )
+
+
+
+# Assuming 'hansard_corpus' is already loaded
+# Convert variables to factors
+hansard_corpus <- hansard_corpus %>%
+  mutate(
+    interject = as.factor(interject),  # Ensure 'interject' is a factor for logistic regression
+    gender = as.factor(gender),
+    party = as.factor(party),
+    in.gov = as.factor(in.gov),
+    year = as.numeric(format(as.Date(date, format = "%Y-%m-%d"), "%Y"))  # Extract year from date
+  )
+
+# Check for any NA values and decide how to handle them
+hansard_corpus1 <- na.omit(hansard_corpus)  # This line removes rows with any NA values
+
+
+# Load the stats package for logistic regression
+library(stats)
+
+# Fit logistic regression model
+logit_model <- glm(interject ~ gender + year + party + in.gov, data = hansard_corpus1, family = binomial())
+
+# Display the summary of the model
+summary(logit_model)
+
+```
+
+#### Save model ####
+saveRDS(
+  first_model,
+  file = "models/first_model.rds"
+)
+
+

### 2025-01-15 scripts/00-simulate_data.R
more changes

@@ -28,7 +28,3 @@ data <- tibble(
 
 #### Save data ####
 write_csv(data, "data/00-simulated_data/simulated_data.csv")
-
-
-
-print(nrow(data))  # This should output 100 if the data generation is correct

### 2025-01-15 data/01-raw_data/Raw Data Availability Notice.R
update the data availability notice

@@ -1,0 +1,6 @@
+#Due to the large size of the required dataset, it is not feasible to host it
+ #directly on GitHub. To ensure the repository remains efficient and accessible,
+ #we have not included the dataset files within the GitHub repository. To access 
+ #the dataset, please run the scripts and download the raw dataset directly to 
+ #your local system. 
+

### 2025-01-15 data/02-analysis_data/Analysis Data Availability Notice.R

@@ -1,0 +1,5 @@
+#Due to the large size of the required dataset, it is not feasible to host it
+  #directly on GitHub. To ensure the repository remains efficient and accessible,
+  #we have not included the dataset files within the GitHub repository. To access 
+  #the dataset, please run the scripts and download the cleaned dataset directly 
+  #to your local system. 

### 2025-01-15 scripts/03-clean_data.R
Update 03-clean_data.R

@@ -1,6 +1,6 @@
 #### Preamble ####
 # Purpose: Cleans the raw data 
-# Author: Rohan Alexander Hannah Yu
+# Author: Rohan Alexander, Hannah Yu
 # Date: 2 October, 2024
 # Contact: rohan.alexander@utoronto.ca, realhannah.yu@mail.utoronto.ca
 # License: MIT

### 2025-01-15 paper/paper.qmd
update paper name

@@
 ---
-title: "Gender Dynamics of Parliamentary Interruptions: A Detailed Analysis of Speech Disruptions in the Australian Parliament (1998-2022)"
+title: "Silenced in the Chamber: Analyzing Gendered Speech Interruptions in the Australian Parliament (1998–2022)"
 subtitle: "My subtitle if needed"

### 2025-01-15 paper/paper.qmd
more changes

@@
 title: "Silenced in the Chamber: Analyzing Gendered Speech Interruptions in the Australian Parliament (1998–2022)"
-subtitle: "My subtitle if needed"
 author: 
@@
 ```{r}
+#| include: false
 #| warning: false
@@
 
-# Introduction
-
-Overview paragraph
-
-Estimand paragraph
-
-Results paragraph
-
-Why it matters paragraph
-
-Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....
-git config --global http.postBuffer 524288000
-
-git config --global http.postBuffer 629145600
-
-git reset --soft HEAD~1
-
-git lfs install
-git lfs track "*.parquet"
-git add .gitattributes
-git commit -m "Track large parquet files with Git LFS"
-git add data/01-raw_data/hansard-corpus/hansard_corpus_1998_to_2022.parquet
-git commit -m "Add large Hansard Parquet file"
-git push origin main
-
 ## Overview
@@
 
-# Results
-
 # Discussion

### 2025-01-24 paper/paper.qmd
built model and wrote data and changed structure

@@
 
-# Data {#sec-data}
-
-# Model {#sec-model}
-# Results {#sec-results}
-
 ```{r}
@@
 
+# Data {#sec-data}
+Data analysis is performed using statistical programming language R [@citeR], with packages `tidyverse` [@citeTidyverse], `arrow` [@citeArrow]`, here` [@citeHere], `rstanarm` [@rstanarm], `modelsummary` [@citeModleSummary], `ggplot2` [@citeGgplot2], `knitr` [@citeKnitr], `tibble` [@citeTibble], `gt` [@citegt], `patchwork` [@citePatchwork], `testthat` [@citetestthat], `kableExtra` [@citeKableExtra], `dyplyr` [@citedplyr], `stringr` [@citestringr], and `lubridate` [@citelubridate].
+
+## Data Source
+
+The data used in this research is a compiled digital record of the Australian Hansard that documents parliamentary proceedings from 1998 t0 2022 [@KatzAlexander2022].
+This comprehensive database includes variables such as speaker details (e.g., name, party, gender, electorate), timestamps, speech content, and flags for interjections, questions, and other procedural elements.
+This dataset is favoured for its utility in examining parliamentary gender dynamics, speech patterns, and the evolution of political discourse over an extensive period.
+
+## Data Cleaning
+
+## Measurement
+The Hansard dataset represents various real-world parliamentary phenomena through carefully constructed variables.
+However, as with all datasets, some considerations and limitations arise when transitioning from real-world events to structured data.
+This section discusses what the variables of interest are measuring and potential challenges in their representation.
+
+Firstly, the variable interject, which indicates whether a speaker’s statement was interrupted, relies on the identification of interruptions as recorded in the Hansard transcripts.
+However, the variable may not fully capture the intent or context of interruptions, as it cannot distinguish between interruptions made in jest, as points of order, or as serious challenges.
+Additionally, subtle interruptions not formally acknowledged in the record or overlapping statements may go unflagged.
+
+The variable gender, representing the speaker's gender, was inferred by merging the dataset with external biographical sources, such as the AustralianPoliticians package.
+While this approach ensures consistency, it assumes the accuracy of external data sources, which may contain errors or outdated information.
+Furthermore, the binary classification of gender in the dataset does not account for non-binary or other gender identities, potentially limiting the scope of gender-based analyses.
+
+The party variable categorizes speakers by their political affiliation.
+This information is directly parsed from the Hansard transcripts, where the party name or abbreviation is provided alongside the speaker's details.
+However, variations in party naming conventions, particularly for smaller or region-specific parties, required standardization using external datasets like Party Facts.
+These efforts may introduce minor inconsistencies, especially in cases of historical party name changes or mergers.
+
+Lastly, word_count quantifies the length of each speech by counting the number of words in the speech text.
+While straightforward to compute, this variable does not differentiate between substantive contributions and procedural or repetitive language.
+Additionally, transcription errors or inconsistencies in the Hansard record might slightly affect word count accuracy, though these are rare.
+
+Overall, while the variables provide meaningful representations of parliamentary behavior, they are shaped by the limitations of transcription accuracy, data inference, and structural simplifications inherent in processing complex real-world phenomena.
+
+## Outcome Variables
+
 ```{r}
@@
 ```
+
+```{r}
+#| include: false
+#| warning: false
+#| message: false
+#Based on the following data it shows that in fact men seem to be interrupted more on avergae than women in the australian parliment, but this could be changed from the "unknown" category.
+# Summarize interruptions by year and gender
+interruptions_summary <- hansard_corpus %>%
+  group_by(year, gender) %>%
+  summarise(
+    total_interruptions = sum(as.numeric(interject), na.rm = TRUE),
+    .groups = 'drop'
+  )
+
+# Summarize total interruptions for all genders combined per year
+interruptions_all <- hansard_corpus %>%
+  group_by(year) %>%
+  summarise(
+    total_interruptions = sum(as.numeric(interject), na.rm = TRUE),
+    .groups = 'drop'
+  ) %>%
+  mutate(
+    gender = "All"
+  )
+
+# Combine gender-specific and "All" categories data
+final_data <- bind_rows(interruptions_summary, interruptions_all)
+
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| label: fig-1
+#| fig-cap: "Yearly Interruptions in Australian Parliament by Gender"
+
+ggplot(final_data, aes(x = year, y = total_interruptions, color = gender)) +
+  geom_line(size = 1.2) +  # Thicker lines for better visibility
+  geom_point(size = 2) +  # Larger points to highlight data
+  labs(
+    title = "Yearly Interruptions in Australian\nParliament by Gender",
+    x = "Year",
+    y = "Total Interruptions",
+    color = "Gender"
+  ) +
+  scale_color_brewer(palette = "Set2") +  # Use a colorblind-friendly palette
+  theme_minimal(base_size = 14) +  # Adjust base font size for readability
+  theme(
+    legend.position = "top",  # Move legend to the top
+    legend.title = element_text(size = 10, face = "bold"),  # Bold legend title
+    legend.text = element_text(size = 8),  # Adjust legend text size
+    plot.title = element_text(size = 14, face = "bold",  hjust = 0.5),  # Bold title
+    axis.title = element_text(size = 12),  # Axis title size
+    axis.text = element_text(size = 11)  # Axis text size
+  ) +
+  scale_x_continuous(breaks = seq(min(final_data$year), max(final_data$year), by = 5))  # Adjust x-axis breaks
+
+```
+
+```{r}
+#| include: false
+#| warning: false
+#| message: false
+
+# Ensure that 'date' is correctly formatted as Date and 'year' is extracted
+hansard_corpus <- hansard_corpus %>%
+  mutate(
+    date = as.Date(date, format = "%Y-%m-%d"),  # Convert date if it's in character form
+    year = if_else(is.na(date), NA_integer_, year(date))  # Extract year, handle NA dates
+  )
+
+# Assuming hansard_corpus has the year extracted already. If not, add this in the mutate step.
+interruptions_by_year_gender <- hansard_corpus %>%
+  group_by(year, gender) %>%
+  summarise(
+    total_interruptions = sum(interject, na.rm = TRUE),
+    total_speeches = n(),
+    .groups = 'drop'
+  ) %>%
+  mutate(
+    interruption_proportion = total_interruptions / total_speeches
+  )
+
+# Calculate for all genders per year
+interruptions_by_year_all <- hansard_corpus %>%
+  group_by(year) %>%
+  summarise(
+    total_interruptions = sum(interject, na.rm = TRUE),
+    total_speeches = n(),
+    .groups = 'drop'
+  ) %>%
+  mutate(
+    gender = "All",
+    interruption_proportion = total_interruptions / total_speeches
+  )
+
+# Combine data
+final_data1 <- bind_rows(interruptions_by_year_gender, interruptions_by_year_all)
+
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| label: fig-2
+#| fig-cap: "Yearly Interruptions Proportions in Australian Parliament by Gender"
+
+ggplot(final_data1, aes(x = year, y = interruption_proportion, color = gender)) +
+  geom_line(size = 1.2) +  # Thicker lines for better visibility
+  geom_point(size = 2) +  # Larger points to highlight data
+  labs(
+    title = "Yearly Interruptions Proportions\nin Australian Parliament by Gender",  # Add \n for a line break
+    x = "Year",
+    y = "Total Interruptions Proportions",
+    color = "Gender"
+  ) +
+  scale_color_brewer(palette = "Set2") +  # Use a colorblind-friendly palette
+  theme_minimal(base_size = 14) +  # Adjust base font size for readability
+  theme(
+    legend.position = "top",  # Move legend to the top
+    legend.title = element_text(size = 10, face = "bold"),  # Bold legend title
+    legend.text = element_text(size = 8),  # Adjust legend text size
+    plot.title = element_text(size = 14, face = "bold", hjust = 0.5),  # Center the title
+    axis.title = element_text(size = 12),  # Axis title size
+    axis.text = element_text(size = 11)  # Axis text size
+  ) +
+  scale_x_continuous(breaks = seq(min(final_data$year), max(final_data$year), by = 5))  # Adjust x-axis breaks
+
+```
+
+The outcome variable, interject, serves as a binary indicator of whether a speaker was interrupted during their speech.
+To explore the distributions of interruptions over years, we introduce the following plots.
+@fig-1 illustrates interruptions in the Australian Parliament from 1998 to 2022, categorized by gender.
+Notably, male speakers consistently faced more interruptions than females, with a peak in 2011 and a subsequent decline.
+Female speakers experienced fewer interruptions, with relatively stable figures across the years.
+The "Unknown" category, consistently low, suggests either minimal occurrence or documentation of such interruptions.
+
+To provide a fair comparison of interruptions across different genders within the Australian Parliament, we normalize the data by calculating proportions.
+This method addresses the gender imbalance in parliament, ensuring that the analysis reflects the frequency of interruptions relative to each gender's representation.
+@fig-2 presents the proportions of speeches interrupted by gender.
+It indicates that male speakers had a higher proportion of their speeches interrupted, especially during the mid-2000s to early 2010s, though the gap between genders has narrowed over time.
+The proportion of interruptions for female speakers generally mirrors these fluctuations, implying that specific topics or periods may have incited more active parliamentary interactions.
+The "Unknown" gender shows minimal changes, highlighting its limited data representation.
+This analysis points out both the consistency and evolution of gender dynamics within parliamentary debates over the years.
+
+## Predictor Variables
 
@@
 
+The predictor variables in this analysis capture key characteristics and contextual factors that may influence the likelihood of interruptions during parliamentary speeches.
+Gender represents the speaker's gender, allowing us to examine whether men and women experience interruptions at different rates.
+Party indicates the speaker's political affiliation, reflecting potential partisan dynamics that could impact speech interactions.
+The government status variable identifies whether the speaker belongs to the governing party, which may affect their level of authority or the degree of scrutiny they face from the opposition.
+Lastly, the word count quantifies the length of each speech, providing insight into whether longer speeches are more likely to invite interruptions.
+Together, these variables offer a comprehensive framework for understanding how personal and contextual factors contribute to the dynamics of parliamentary discourse.
+
 @tbl-1 provides a clear view of the proportion of interruptions by gender across all speeches in the dataset.
@@
 #| message: false
-#Based on the following data it shows that in fact men seem to be interrupted more on avergae than women in the australian parliment, but this could be changed from the "unknown" category.
-# Summarize interruptions by year and gender
-interruptions_summary <- hansard_corpus %>%
-  group_by(year, gender) %>%
-  summarise(
-    total_interruptions = sum(as.numeric(interject), na.rm = TRUE),
-    .groups = 'drop'
-  )
-
-# Summarize total interruptions for all genders combined per year
-interruptions_all <- hansard_corpus %>%
-  group_by(year) %>%
-  summarise(
-    total_interruptions = sum(as.numeric(interject), na.rm = TRUE),
-    .groups = 'drop'
-  ) %>%
-  mutate(
-    gender = "All"
-  )
-
-# Combine gender-specific and "All" categories data
-final_data <- bind_rows(interruptions_summary, interruptions_all)
+print(final_data1)
 
@@
 #| message: false
-#| label: fig-1
-#| fig-cap: "Yearly Interruptions in Australian Parliament by Gender"
-
-ggplot(final_data, aes(x = year, y = total_interruptions, color = gender)) +
-  geom_line(size = 1.2) +  # Thicker lines for better visibility
-  geom_point(size = 2) +  # Larger points to highlight data
-  labs(
-    title = "Yearly Interruptions in Australian\nParliament by Gender",
-    x = "Year",
-    y = "Total Interruptions",
-    color = "Gender"
-  ) +
-  scale_color_brewer(palette = "Set2") +  # Use a colorblind-friendly palette
-  theme_minimal(base_size = 14) +  # Adjust base font size for readability
-  theme(
-    legend.position = "top",  # Move legend to the top
-    legend.title = element_text(size = 10, face = "bold"),  # Bold legend title
-    legend.text = element_text(size = 8),  # Adjust legend text size
-    plot.title = element_text(size = 14, face = "bold",  hjust = 0.5),  # Bold title
-    axis.title = element_text(size = 12),  # Axis title size
-    axis.text = element_text(size = 11)  # Axis text size
-  ) +
-  scale_x_continuous(breaks = seq(min(final_data$year), max(final_data$year), by = 5))  # Adjust x-axis breaks
-
-```
-
-```{r}
-#| include: false
-#| warning: false
-#| message: false
-
-# Ensure that 'date' is correctly formatted as Date and 'year' is extracted
-hansard_corpus <- hansard_corpus %>%
-  mutate(
-    date = as.Date(date, format = "%Y-%m-%d"),  # Convert date if it's in character form
-    year = if_else(is.na(date), NA_integer_, year(date))  # Extract year, handle NA dates
-  )
-
-# Assuming hansard_corpus has the year extracted already. If not, add this in the mutate step.
-interruptions_by_year_gender <- hansard_corpus %>%
-  group_by(year, gender) %>%
-  summarise(
-    total_interruptions = sum(interject, na.rm = TRUE),
-    total_speeches = n(),
-    .groups = 'drop'
-  ) %>%
-  mutate(
-    interruption_proportion = total_interruptions / total_speeches
-  )
-
-# Calculate for all genders per year
-interruptions_by_year_all <- hansard_corpus %>%
-  group_by(year) %>%
-  summarise(
-    total_interruptions = sum(interject, na.rm = TRUE),
-    total_speeches = n(),
-    .groups = 'drop'
-  ) %>%
-  mutate(
-    gender = "All",
-    interruption_proportion = total_interruptions / total_speeches
-  )
-
-# Combine data
-final_data1 <- bind_rows(interruptions_by_year_gender, interruptions_by_year_all)
-
-```
-
-```{r}
-#| echo: false
-#| warning: false
-#| message: false
-#| label: fig-2
-#| fig-cap: "Yearly Interruptions Proportions in Australian Parliament by Gender"
-
-ggplot(final_data1, aes(x = year, y = interruption_proportion, color = gender)) +
-  geom_line(size = 1.2) +  # Thicker lines for better visibility
-  geom_point(size = 2) +  # Larger points to highlight data
-  labs(
-    title = "Yearly Interruptions Proportions\nin Australian Parliament by Gender",  # Add \n for a line break
-    x = "Year",
-    y = "Total Interruptions Proportions",
-    color = "Gender"
-  ) +
-  scale_color_brewer(palette = "Set2") +  # Use a colorblind-friendly palette
-  theme_minimal(base_size = 14) +  # Adjust base font size for readability
-  theme(
-    legend.position = "top",  # Move legend to the top
-    legend.title = element_text(size = 10, face = "bold"),  # Bold legend title
-    legend.text = element_text(size = 8),  # Adjust legend text size
-    plot.title = element_text(size = 14, face = "bold", hjust = 0.5),  # Center the title
-    axis.title = element_text(size = 12),  # Axis title size
-    axis.text = element_text(size = 11)  # Axis text size
-  ) +
-  scale_x_continuous(breaks = seq(min(final_data$year), max(final_data$year), by = 5))  # Adjust x-axis breaks
-
-```
-
-@fig-1 illustrates interruptions in the Australian Parliament from 1998 to 2022, categorized by gender.
-Notably, male speakers consistently faced more interruptions than females, with a peak in 2011 and a subsequent decline.
-Female speakers experienced fewer interruptions, with relatively stable figures across the years.
-The "Unknown" category, consistently low, suggests either minimal occurrence or documentation of such interruptions.
-
-To provide a fair comparison of interruptions across different genders within the Australian Parliament, we normalize the data by calculating proportions.
-This method addresses the gender imbalance in parliament, ensuring that the analysis reflects the frequency of interruptions relative to each gender's representation.
-@fig-2 presents the proportions of speeches interrupted by gender.
-It indicates that male speakers had a higher proportion of their speeches interrupted, especially during the mid-2000s to early 2010s, though the gap between genders has narrowed over time.
-The proportion of interruptions for female speakers generally mirrors these fluctuations, implying that specific topics or periods may have incited more active parliamentary interactions.
-The "Unknown" gender shows minimal changes, highlighting its limited data representation.
-This analysis points out both the consistency and evolution of gender dynamics within parliamentary debates over the years.
-
-```{r}
-#| include: false
-#| warning: false
-#| message: false
-print(final_data1)
-
-```
-
-```{r}
-#| echo: false
-#| warning: false
-#| message: false
-#| label: fig-2_chamber
-#| fig-cap: "Yearly Interruptions Proportions in Australian Parliament by Gender (Chamber)"
-
-no_fedchamb <- hansard_corpus %>%
-  filter(fedchamb_flag == 0)
-
-# Group by year and gender to summarize interruptions
-interruptions_by_year_gender <- no_fedchamb %>%
-  group_by(year, gender) %>%
-  summarise(
-    total_interruptions = sum(interject, na.rm = TRUE),
-    total_speeches = n(),
-    .groups = 'drop'
-  ) %>%
-  mutate(
-    interruption_proportion = total_interruptions / total_speeches
-  )
-
-# Calculate interruptions for all genders combined per year
-interruptions_by_year_all <- no_fedchamb %>%
-  group_by(year) %>%
-  summarise(
-    total_interruptions = sum(interject, na.rm = TRUE),
-    total_speeches = n(),
-    .groups = 'drop'
-  ) %>%
-  mutate(
-    gender = "All",
-    interruption_proportion = total_interruptions / total_speeches
-  )
-
-# Combine the gender-specific and overall data
-final_data2 <- bind_rows(interruptions_by_year_gender, interruptions_by_year_all)
-
-# Plotting the interruptions proportions by year and gender
-ggplot(final_data2, aes(x = year, y = interruption_proportion, color = gender)) +
-  geom_line(size = 1.2) +  # Use thicker lines for better visibility
-  geom_point(size = 2) +  # Use larger points to highlight data points
-  labs(
-    title = "Yearly Interruptions Proportions\nin Australian Parliament by Gender (Chamber)",
-    x = "Year",
-    y = "Total Interruptions Proportions",
-    color = "Gender"
-  ) +
-  scale_color_brewer(palette = "Set2") +  # Use a colorblind-friendly palette
-  theme_minimal(base_size = 14) +  # Use a minimal theme with readable base font size
-  theme(
-    legend.position = "top",  # Position legend at the top for better accessibility
-    legend.title = element_text(size = 10, face = "bold"),  # Bold the legend title
-    legend.text = element_text(size = 8),  # Set legend text size
-    plot.title = element_text(size = 14, face = "bold", hjust = 0.5),  # Center and bold the plot title
-    axis.title = element_text(size = 12),  # Set axis title size
-    axis.text = element_text(size = 11)  # Set axis text size
-  ) +
-  scale_x_continuous(breaks = seq(min(final_data$year), max(final_data$year), by = 5))  # Set x-axis breaks every 5 years
-
-```
-```{r}
-#| include: false
-#| warning: false
-#| message: false
-# Displaying the table of final data
-print(final_data2)
-
-```
-
-```{r}
-#| include: false
-#| warning: false
-#| message: false
-# Pivot to get male and female data on the same row
-comparison_data <- final_data2 %>%
+#| tbl-cap: "Gender Interruption Proportions Annual Comparison"
+#| label: tbl-compareyear
+
+# Prepare the data
+comparison_data <- final_data1 %>%
   pivot_wider(
@@
     values_from = interruption_proportion
-  )
-
-# Determine which gender had more interruptions per year
-yearly_comparison <- comparison_data %>%
-  mutate(
-    More_Interrupted_Gender = case_when(
-      Male > Female ~ "Male",
-      Female > Male ~ "Female",
-      TRUE ~ "Equal"
-    )
-  )
-
-# Count the number of years each gender was interrupted more
-gender_counts <- yearly_comparison %>%
-  count(More_Interrupted_Gender)
-
-```
-
-```{r}
-#| include: false
-#| warning: false
-#| message: false
-# Determine which gender had more interruptions per year
-yearly_comparison <- comparison_data %>%
+  ) %>%
   mutate(
@@
     )
-  ) %>%
-  select(year, More_Interrupted_Gender)  # Select only the year and the more interrupted gender columns
-
-# Print the simplified table
-print(yearly_comparison)
-```
-
-```{r}
-#| echo: false
-#| warning: false
-#| message: false
-#| tbl-cap: "Gender Interruption Proportions Annual Comparison Across General and Chamber"
-#| label: tbl-compareyear
-# Prepare the data
-comparison_all <- final_data1 %>%
-  pivot_wider(
-    id_cols = year,
-    names_from = gender,
-    values_from = interruption_proportion
-  ) %>%
-  mutate(
-    More_Interrupted_Gender_All = case_when(
-      Male > Female ~ "Male",
-      Female > Male ~ "Female",
-      TRUE ~ "Equal"
-    )
-  )
-
-comparison_chamber <- final_data2 %>%
-  pivot_wider(
-    id_cols = year,
-    names_from = gender,
-    values_from = interruption_proportion
-  ) %>%
-  mutate(
-    More_Interrupted_Gender_Chamber = case_when(
-      Male > Female ~ "Male",
-      Female > Male ~ "Female",
-      TRUE ~ "Equal"
-    )
-  )
-
-# Assuming final_comparison is prepared as follows
-final_comparison <- comparison_all %>%
-  select(year, More_Interrupted_Gender_All) %>%
-  left_join(comparison_chamber %>% select(year, More_Interrupted_Gender_Chamber), by = "year")
-
-final_comparison %>%
-  gt %>%
+  )
+
+# Generate the table using gt
+comparison_data %>%
+  select(year, More_Interrupted_Gender) %>%  # Include only year and the gender comparison
+  gt() %>%
   cols_label(
     year = "Year",
-    More_Interrupted_Gender_All = "More Interrupted Gender All",
-    More_Interrupted_Gender_Chamber = "More Interrupted Gender Chamber")%>%
+    More_Interrupted_Gender = "More Interrupted Gender"
+  ) %>%
   tab_style(
@@
 ```
-
-```{r}
-#| echo: false
-#| warning: false
-#| message: false
-#| label: fig-compare
-#| fig-cap: "Yearly Interruptions Proportions in Australian Parliament by Gender"
-
-# Original dataset, no condition on fedchamb_flag
-interruptions_original <- hansard_corpus %>%
-  filter(gender %in% c("Male", "Female")) %>%
-  mutate(
-    date = as.Date(date, format = "%Y-%m-%d"),
-    year = if_else(is.na(date), NA_integer_, year(date))
-  ) %>%
-  group_by(year, gender) %>%
-  summarise(
-    total_interruptions = sum(interject, na.rm = TRUE),
-    total_speeches = n(),
-    .groups = 'drop'
-  ) %>%
-  mutate(
-    interruption_proportion = total_interruptions / total_speeches,
-    condition = "All Data"
-  )
-
-# Dataset with fedchamb_flag == 0
-interruptions_fedchamb_flag_0 <- hansard_corpus %>%
-  filter(gender %in% c("Male", "Female"), fedchamb_flag == 0) %>%
-  mutate(
-    date = as.Date(date, format = "%Y-%m-%d"),
-    year = if_else(is.na(date), NA_integer_, year(date))
-  ) %>%
-  group_by(year, gender) %>%
-  summarise(
-    total_interruptions = sum(interject, na.rm = TRUE),
-    total_speeches = n(),
-    .groups = 'drop'
-  ) %>%
-  mutate(
-    interruption_proportion = total_interruptions / total_speeches,
-    condition = "fedchamb_flag = 0"
-  )
-
-# Combine the datasets
-final_data3 <- bind_rows(interruptions_original, interruptions_fedchamb_flag_0)
-
-# Adjust labels for condition and linetype
-ggplot(final_data3, aes(x = year, y = interruption_proportion, color = gender, linetype = condition)) +
-  geom_line(size = 1.2) +
-  geom_point(size = 2) +
-  labs(
-    title = "Yearly Interruptions Proportions in\nAustralian Parliament by Gender",
-    subtitle = "Comparing All Data vs. Chamber Data Only",
-    x = "Year",
-    y = "Interruption Proportion",
-    color = "Gender",
-    linetype = "Dataset Type"
-  ) +
-  scale_color_brewer(palette = "Set2") +
-  scale_linetype_manual(values = c("solid", "dotted"), 
-                        labels = c("All", "Chamber")) +
-  theme_minimal(base_size = 14) +
-  theme(
-    legend.position = "top",
-    legend.title = element_text(size = 10, face = "bold"),
-    legend.text = element_text(size = 8),
-    plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
-    plot.subtitle = element_text(size = 12, face = "italic", hjust = 0.5),
-    axis.title = element_text(size = 12),
-    axis.text = element_text(size = 11)
-  ) +
-  scale_x_continuous(breaks = seq(min(final_data3$year), max(final_data3$year), by = 5))  # Adjust x-axis breaks
-
-```
-
-Only analyzing Chamber members, @fig-2_chamber again illustrates interruptions in the Australian Parliament from 1998 to 2022, categorized by gender.
-To distinguish the differences across the two figures, @fig-compare contains both the interruptions for all data and Chamber member data.
-While the interruption patterns in the chamber-only data in @fig-2_chamber largely mirror those observed in the comprehensive dataset @fig-2, there are slight increases in the interruption proportions for women, indicating a potentially heightened level of disruption experienced by female members in non-federal chambers.
 
@@
 #| message: false
-#| tbl-cap: "Interruption Summary by Government Status (All)"
+#| tbl-cap: "Interruption Summary by Government Status"
 #| label: tbl-ingov1
@@
 # Create a clean and professional table
-interruption_summary %>%
-  gt() %>%
-  tab_style(
-    style = cell_text(align = "left"),  # Align text to the left
-    locations = cells_body(columns = everything())  # Apply to all columns in the body
-  )
-
-```
-
-```{r}
-#| echo: false
-#| warning: false
-#| message: false
-#| tbl-cap: "Interruption Summary by Government Status in Non-Federal Chamber Sessions"
-#| label: tbl-ingov2
-
-# Assume that interruption_summary is already prepared as previously coded
-interruption_summary <- hansard_corpus %>%
-  filter(fedchamb_flag == 0) %>%
-  mutate(
-    in_gov = factor(in.gov, levels = c(0, 1), labels = c("In Opposition", "In Government")),
-    interject = factor(interject, levels = c(0, 1), labels = c("No", "Yes"))
-  ) %>%
-  group_by(in_gov, interject) %>%
-  summarise(
-    Count = n(),
-    .groups = 'drop'
-  ) %>%
-  arrange(in_gov, desc(interject)) %>%
-  rename(
-    `Government Status` = in_gov,
-    `Interruption` = interject,
-    `Count` = Count
-  )
 interruption_summary %>%
@@
 ```{r}
-#| echo: false
+#| include: false
 #| warning: false
@@
 #| message: false
-# Filter and aggregate data based on the 'question' flag and 'gender'
+# Filter and aggregate data based on the 'answer' flag and 'gender'
 interruptions_question_analysis <- hansard_corpus %>%
@@
 #| message: false
+#| label: fig-density
+#| fig-cap: "Density Distribution of Word Count by Gender"
+# Filter the data to include only speeches with word counts under 500 and valid gender values
+filtered_data <- hansard_corpus %>%
+  filter(word_count <= 500, gender != "Unknown")
+
+# Create the density plot with boundary outlines
+ggplot(filtered_data, aes(x = word_count, fill = gender, color = gender)) +
+  geom_density(alpha = 0.5) +
+  scale_fill_manual(
+    values = c("Female" = "pink", "Male" = "lightblue")
+  ) +
+  scale_color_manual(
+    values = c("Female" = "red", "Male" = "blue")
+  ) +
+  labs(
+    title = "Density Distribution of Word Count by Gender (Word Count ≤ 500)",
+    x = "Word Count",
+    y = "Density",
+    fill = "Gender",
+    color = "Gender"
+  ) +
+  theme_minimal() +
+  theme(
+    plot.title = element_text(hjust = 0.5),  # Center the title
+    legend.position = "right"               # Place the legend to the right
+  )
+
+```
+The density plot @fig-density shows that the word count distribution for both male and female speakers is highly left-skewed, with the majority of speeches being very short.
+Both genders peak at shorter speeches, but male speakers tend to have even shorter speeches compared to females, as indicated by the higher peak density for men in the lower word count range.
+Notably, female speakers show a small rise in density between word counts of 200 and 300, suggesting that a subset of their speeches tends to be slightly longer compared to their male counterparts.
+This subtle difference highlights variation in speaking patterns between genders.
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
 #| label: tbl-gov4
@@
 
-```{r}
-#| echo: false
-#| warning: false
-#| message: false
-#| label: fig-gov5
-#| fig-cap: "Gender-Based Interruptions and Word Count"
-# Bar plot for total speeches with real numbers on the y-axis
-ggplot(summary_table, aes(x = gender, y = average_words, fill = factor(interject))) +
-  geom_bar(stat = "identity", position = "dodge") +
-  scale_fill_manual(values = c("steelblue", "salmon"), labels = c("No", "Yes")) +
-  scale_y_continuous(labels = scales::comma) +  # Display real numbers on the y-axis
-  labs(
-    title = "Gender-Based Interruptions and Word Count",
-    x = "Gender",
-    y = "Total Speeches",
-    fill = "Interruption"
-  ) +
-  theme_minimal(base_size = 14) +
-  theme(
-    legend.position = "top",
-    plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
-    axis.title = element_text(size = 12),
-    axis.text = element_text(size = 10)
-  )
-
-```
-@tbl-gov4 and @fig-gov5 highlights that, on average, females tend to speak longer than males before an interruption occurs.
+@tbl-gov4 highlights that, on average, females tend to speak longer than males before an interruption occurs.
 For uninterrupted speeches, females average 560.72 words compared to 448.67 words for males.
@@
 
+# Model {#sec-model}
+## Model set-up
+
+I utilized a Bayesian logistic regression model to examine the relationship between speech interruptions and the speakers' genders. The model is formulated as follows:
+
+\begin{align}
+y_i|\pi_i &\sim \mbox{Bern}(\pi_i) \\
+\mbox{logit}(\pi_i) &= \alpha + \beta_1 \times \mbox{gender}_i + \beta_2 \times \mbox{party}_i + \beta_3 \times \mbox{word\_count}_i + \beta_4 \times \mbox{word\_count\_gender}_i \nonumber \\
+\alpha &\sim \mbox{Normal}(0, 5) \nonumber \\
+\beta_1 &\sim \mbox{Normal}(0, 2.5) \nonumber \\
+\beta_2 &\sim \mbox{Normal}(0, 2.5) \nonumber \\
+\beta_3 &\sim \mbox{Normal}(0, 2.5) \nonumber \\
+\beta_4 &\sim \mbox{Normal}(0, 2.5) \nonumber
+\end{align}
+
+# Results {#sec-results}
+```{r}
+#| include: false
+#| eval: true
+#| warning: false
+#| message: false
+
+model1 <-
+  readRDS(file = here::here("models/model1.rds"))
+
+```
+
+```{r}
+#| echo: false
+#| eval: true
+#| label: tbl-modelresults1
+#| tbl-cap: "Model 1 for Interruptions (n = 1000)"
+#| warning: false
+
+modelsummary(
+  list(
+    "Speech Interrupted" = model1
+  ),
+  statistic = "mad"
+  )
+```
+
+@tbl-modelresults1 identifies key predictors including gender, party, and word count of speech interruptions in parliamentary proceedings.
+Gender plays an important role, with male speakers more likely to experience interruptions compared to female speakers.
+This suggests that men face slightly higher odds of interjections during their speeches.
+Party affiliation also significantly influences interruptions, with some parties, such as the ALP, experiencing more frequent interjections, while others, like the LNP, are interrupted less often.
+These patterns highlight how political dynamics can shape interactions in debates.
+
+Additionally, the length of speeches affects interruptions, with longer speeches slightly less likely to be interrupted, suggesting that concise speeches may invite more interjections.
+Notably, the interaction between word count and gender reveals that male speakers experience a slight increase in interruptions as their speech length increases, a trend that is less pronounced for female speakers.
+These findings underscore the combined effects of gender, party dynamics, and speech characteristics in shaping interruption patterns.
+
+```{r}
+#| include: false
+
+library(modelsummary)
+
+# Generate the modelsummary table with significance stars and custom formatting
+modelsummary(
+  list(
+    "Speech Interrupted" = model1
+  ),
+  statistic = "({std.error})",           # Include standard errors in parentheses
+  stars = TRUE,                          # Add significance stars
+  output = "markdown",                   # Choose the desired output format (e.g., "latex", "html", "markdown")
+  title = "Logistic Regression: Predicting Speech Interruption",
+  coef_map = c(                          # Rename variables for clarity
+    "(Intercept)" = "Intercept",
+    "gender" = "Gender (Female)",
+    "party" = "Party Affiliation",
+    "word_count" = "Word Count",
+    "word_count_gender" = "Word Count × Gender"
+  )
+)
+
+```
+
+```{r}
+#| include: false
+#| eval: true
+#| warning: false
+#| message: false
+model2 <-
+  readRDS(file = here::here("models/model2.rds"))
+
+```
+
+```{r}
+#| echo: false
+#| eval: true
+#| label: tbl-modelresults2
+#| tbl-cap: "Model 2 for Interruptions (n = 1000)"
+#| warning: false
+
+modelsummary(
+  list(
+    "Speech Interrupted" = model2
+  ),
+  statistic = "mad"
+  )
+```
+
+The logistic regression model @tbl-modelresults2 continues to highlight key predictors of interruptions during speeches, with the removal of party.
+Male speakers remain more likely to experience interruptions than female speakers, but the effect size has slightly decreased, reflecting a smaller increase in the likelihood of interruptions.
+The relationship between speech length and interruptions remains consistent, with longer speeches slightly reducing the likelihood of interruptions.
+The interaction between word count and gender also remains unchanged, suggesting that longer speeches by male speakers are still slightly more likely to invite interruptions compared to those by females.
+
+### Model justification
+
+We expect a positive relationship between the size of the wings and time spent aloft. In particular...
+
+We can use maths by including latex between dollar signs, for instance $\theta$.
+
 # Discussion {#sec-discussion}
 
-## Overview
-
-## Measurement
-
-Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.
-
-## Outcome variables
-
-Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.
-
-Talk way more about it.
-
-## Predictor variables
-
-Add graphs, tables and text.
-
-Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.
-
-# Model
-
-## Model set-up
-
-Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
-
-\begin{align} 
-y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta &\sim \mbox{Normal}(0, 2.5) \\
-\gamma &\sim \mbox{Normal}(0, 2.5) \\
-\sigma &\sim \mbox{Exponential}(1)
-\end{align}
-
-### Model justification
-
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
-
-We can use maths by including latex between dollar signs, for instance $\theta$.
-
-# Discussion
-
 ## First discussion point {#sec-first-point}

### 2025-01-24 scripts/03-clean_data.R

@@ -13,13 +13,6 @@ library(tidyr)
 library(lubridate)
 #### Clean data ####
 raw_data <- read_parquet("data/01-raw_data/hansard_corpus.parquet")
-head(raw_data, 150)
-
-
-# Explore the Data
-summary(raw_data)
-str(raw_data)
-
 
 raw_data <- raw_data %>%
   mutate(
@@ -33,7 +26,6 @@ raw_data <- raw_data %>%
     )
   )
 
-
 raw_data <- raw_data %>%
   mutate(
     # Convert 'interject' to numeric without changing NA values
@@ -41,7 +33,6 @@ raw_data <- raw_data %>%
     # Correct date format and handle potential date issues
     date = as.Date(date, format="%Y-%m-%d")
   )
-
 
 # Correct Data Types
 raw_data <- raw_data %>%
@@ -52,6 +43,10 @@ raw_data <- raw_data %>%
 
 hansard_corpus$question <- as.numeric(as.character(hansard_corpus$question))
 
+# Filter for only Chamber data and create word count
+raw_data <- raw_data %>%
+  filter(fedchamb_flag == 0) %>%
+  mutate(word_count = str_count(body, "\\b\\w+\\b"))
 
 # Error Checks
 table(raw_data$gender)  # Should only contain known categories

### 2025-01-24 scripts/05-model_data.R

@@ -1,5 +1,5 @@
 #### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
+# Purpose: Models
 # Author: Rohan Alexander, Hannah Yu
 # Date: 14 January 2025
 # Contact: rohan.alexander@utoronto.ca, realhannah.yu@mail.utoronto.ca
@@ -11,56 +11,147 @@
 
 
 #### Workspace setup ####
-library(tidyverse)
+library(dplyr)
 library(rstanarm)
 
 #### Read data ####s
-analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
+analysis_data <- read_parquet("data/02-analysis_data/cleaned_data.parquet")
 
-### Model data ####
-first_model <-
-  stan_glm(
-    formula = flying_time ~ length + width,
-    data = analysis_data,
-    family = gaussian(),
-    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_aux = exponential(rate = 1, autoscale = TRUE),
-    seed = 853
-  )
+set.seed(853)
 
-
-
-# Assuming 'hansard_corpus' is already loaded
-# Convert variables to factors
-hansard_corpus <- hansard_corpus %>%
+sample_data <- analysis_data %>%
+  select(interject, gender, party, word_count) %>% # Select only the desired variables
   mutate(
-    interject = as.factor(interject),  # Ensure 'interject' is a factor for logistic regression
-    gender = as.factor(gender),
-    party = as.factor(party),
-    in.gov = as.factor(in.gov),
-    year = as.numeric(format(as.Date(date, format = "%Y-%m-%d"), "%Y"))  # Extract year from date
+    interject = as.numeric(interject),  # Ensure 'interject' is numeric (binary: 0 or 1)
+    gender = as.factor(gender),         # Convert 'gender' to a factor
+    party = as.factor(party),           # Convert 'party' to a factor
+    word_count = as.numeric(word_count) # Ensure 'word_count' is numeric
   )
 
-# Check for any NA values and decide how to handle them
-hansard_corpus1 <- na.omit(hansard_corpus)  # This line removes rows with any NA values
+# Check the number of rows and columns in the original dataset
+original_rows <- nrow(sample_data)
+original_cols <- ncol(sample_data)
 
 
-# Load the stats package for logistic regression
-library(stats)
+# Count the number of missing values in the original dataset
+na_counts <- sample_data %>%
[…]

### 2025-02-07 paper/paper.qmd
added stm model and bertopic

@@
 
+library(stm)
+library(quanteda)
+library(tm)
 ```
@@
 
+```{r}
+#| include: false
+#| eval: true
+#| warning: false
+#| message: false
+hansard_topics <- readRDS(file = here::here("models/hansard_topics.rda"))
+```
+
+```{r}
+#| echo: false
+#| eval: true
+#| warning: false
+labelTopics(hansard_topics)
+```
+
+To analyze discussions in the Australian Parliament, I applied Structural Topic Modeling (STM) to identify key themes in speeches from 2020.
+The process began with data preprocessing, where I filtered the dataset to include only relevant entries, removed missing values, and structured the text data for analysis.
+A document-feature matrix (DFM) was then created, representing word frequencies while eliminating punctuation, stopwords, and low-frequency terms to improve model efficiency.
+
+The STM model was trained with 10 topics and incorporated party affiliation and speaker gender as prevalence covariates, allowing for an examination of how these factors influence topic distribution.
+The model was optimized over 50 iterations, ensuring convergence and stability.
+The final output provided a breakdown of the dominant topics, with key terms extracted using highest probability words, FREX words (distinctive to each topic), Lift words (rare but highly relevant), and Score words (best summarizing a topic’s meaning).
+
+```{r, fig.width=10, fig.height=6}
+#| echo: false
+#| eval: true
+#| label: tbl-stm_prop
+#| tbl-cap: "STM Topic Proportion Plot "
+#| warning: false
+plot(hansard_topics, type = "summary", n = 5)
+```
+
+@tbl-stm_prop provides an overview of the most prevalent themes in the 2020 Australian parliamentary speeches.
+The x-axis represents the expected topic proportions, indicating how frequently each topic appears across the dataset.
+The y-axis lists the top topics, summarized by their most representative words.
+
+From this visualization, Topic 5 ("minister, government, time, just") emerges as the most dominant theme, suggesting that government policies, ministerial discussions, and legislative matters were central to parliamentary discourse.
+Topic 8 ("people, government, need, now") follows closely, highlighting debates around public needs, government interventions, and social policies.
+Other significant topics include healthcare (Topic 10), economic measures (Topic 4), legal and family-related issues (Topic 7), and national security (Topic 1).
+
+The distribution of topics provides insights into policy priorities and legislative focus areas during 2020.
+By incorporating metadata such as speaker affiliation and gender, further analysis can uncover how different political groups or demographics engaged with these key issues.
+
+```{r}
+#| include: false 
+#par(mar = c(3, 10, 0.2, 1))  # Increase left margin
+#plot(stm_gender, "gender", model = hansard_topics, topics = c(1, 2, 3),
+     #cex = 0.02)  # Reduce text size
+```
+
+```{r}
+#| include: false 
+bertopic_model <- readRDS("models/bertopic_model.rds")
+str(bertopic_model)  # Check structure
+```
+
+```{r}
+str(bertopic_model)
+
+```
+
+```{r}
+#| include: false 
+methods(class = class(bertopic_model))
+names(bertopic_model)
+
+# Convert lists to readable text
+topic_info$Representation <- sapply(topic_info$Representation, function(x) paste(x, collapse=", "))
+topic_info$Representative_Docs <- sapply(topic_info$Representative_Docs, function(x) paste(x, collapse=" | "))
+
+# View the cleaned dataframe
+print(topic_info)
+
+```
+We then applied BERTopic, a powerful topic modeling technique that leverages transformer-based embeddings and clustering methods to extract coherent topics from large text corpora.
+The modeling process involved preprocessing the parliamentary transcripts, fitting the BERTopic model, and visualizing the results to derive insights into the dominant themes discussed.
+
+The initial dataset consisted of Australian parliamentary speeches, which were first filtered to include only those from the year 2020.
+After preprocessing steps such as text cleaning and tokenization, BERTopic was applied to identify underlying topics.
+The model was trained on the speech text, generating a set of distinct topics characterized by their most representative words.
+The results were stored and analyzed to understand the frequency and nature of discussions in parliament.
+
+```{r}
+#| echo: false
+#| eval: true
+#| label: tbl-bert1
+#| tbl-cap: "Most Common Topics in\nParliamentary Speeches (2020)"
+#| warning: false
+
+ggplot(top_topics, aes(x = reorder(Name, Count), y = Count)) +
+  geom_bar(stat = "identity", fill = "steelblue", color = "black") +
+  coord_flip() +
+  labs(
+    title = "Most Common Topics in\nParliamentary Speeches (2020)",
+    x = "Topic",
+    y = "Number of Speeches"
+  ) +
+  theme_minimal(base_size = 14) +
+  theme(
+    plot.title = element_text(size = 14, face = "bold", margin = margin(b = 10)), # Add bottom margin
+    plot.margin = margin(t = 20, r = 20, b = 20, l = 20) # Increase space
+  )
+
+```
+@tbl-bert1 presents the most common topics in parliamentary speeches, ranked by the number of speeches associated with each topic.
+Notably, aged care and homecare, infrastructure and roads, and emergency response to fires emerged as the most frequently discussed themes, reflecting key policy concerns in 2020.
+Other prominent topics included childcare and education, motions and legislative processes, and government economic policies.
+These findings suggest that parliamentary focus was heavily directed toward public services and economic development, particularly in the wake of major national events such as bushfires and the ongoing pandemic response.
+
+```{r}
+#| echo: false
+#| eval: true
+#| label: tbl-bert2
+#| tbl-cap: "Word Cloud"
+#| warning: false
+library(wordcloud)
+
+# Get the most frequent words
+word_freqs <- table(unlist(strsplit(paste(topic_info$Representation, collapse = " "), ", ")))
+
+# Generate word cloud
+wordcloud(names(word_freqs), freq = word_freqs, max.words = 100, colors = brewer.pal(8, "Dark2"))
+
+```
+
+A complementary word cloud further highlights the most frequently occurring words within the parliamentary discussions.
+Terms such as question, minister, interjecting, house, and Morrison suggest a heavy emphasis on political debates, procedural discussions, and executive actions.
+The prominence of words related to economic policies and public welfare indicates that these areas dominated parliamentary discourse in 2020.
+
+By applying BERTopic modeling, I was able to extract and visualize key themes from Australian parliamentary speeches.
+The results indicate a strong focus on public services, infrastructure, legislative procedures, and economic policies, aligning with major political and social developments of that year.
+The combination of ranked topic distributions and textual analysis through the word cloud provides a comprehensive view of how parliamentary discourse was shaped in 2020.
+These findings can be further explored to analyze trends over time or compare discourse across different political actors.
+
 ### Model justification

### 2025-02-07 deletee.R

@@ -1,0 +1,142 @@
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| label: fig-compare
+#| fig-cap: "Yearly Interruptions Proportions in Australian Parliament by Gender"
+
+# Original dataset, no condition on fedchamb_flag
+interruptions_original <- hansard_corpus %>%
+  filter(gender %in% c("Male", "Female")) %>%
+  mutate(
+    date = as.Date(date, format = "%Y-%m-%d"),
+    year = if_else(is.na(date), NA_integer_, year(date))
+  ) %>%
+  group_by(year, gender) %>%
+  summarise(
+    total_interruptions = sum(interject, na.rm = TRUE),
+    total_speeches = n(),
+    .groups = 'drop'
+  ) %>%
+  mutate(
+    interruption_proportion = total_interruptions / total_speeches,
+    condition = "All Data"
+  )
+
+# Dataset with fedchamb_flag == 0
+interruptions_fedchamb_flag_0 <- hansard_corpus %>%
+  filter(gender %in% c("Male", "Female"), fedchamb_flag == 0) %>%
+  mutate(
+    date = as.Date(date, format = "%Y-%m-%d"),
+    year = if_else(is.na(date), NA_integer_, year(date))
+  ) %>%
+  group_by(year, gender) %>%
+  summarise(
+    total_interruptions = sum(interject, na.rm = TRUE),
+    total_speeches = n(),
+    .groups = 'drop'
+  ) %>%
+  mutate(
+    interruption_proportion = total_interruptions / total_speeches,
+    condition = "fedchamb_flag = 0"
+  )
+
+# Combine the datasets
+final_data3 <- bind_rows(interruptions_original, interruptions_fedchamb_flag_0)
+
+# Adjust labels for condition and linetype
+ggplot(final_data3, aes(x = year, y = interruption_proportion, color = gender, linetype = condition)) +
+  geom_line(size = 1.2) +
+  geom_point(size = 2) +
+  labs(
+    title = "Yearly Interruptions Proportions in\nAustralian Parliament by Gender",
+    subtitle = "Comparing All Data vs. Chamber Data Only",
+    x = "Year",
+    y = "Interruption Proportion",
+    color = "Gender",
+    linetype = "Dataset Type"
+  ) +
+  scale_color_brewer(palette = "Set2") +
+  scale_linetype_manual(values = c("solid", "dotted"), 
+                        labels = c("All", "Chamber")) +
[…]

### 2025-02-07 scripts/06-stm.R

@@ -1,0 +1,119 @@
+#### Preamble ####
+# Purpose: Models
+# Author: Rohan Alexander, Hannah Yu
+# Date: 5 Febuary 2025
+# Contact: rohan.alexander@utoronto.ca, realhannah.yu@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: 
+# - 02-download_data.R must have been run
+# - 03-clean_data.R must have been run
+
+
+#### Workspace setup ####
+library(tidyverse)
+library(quanteda)
+library(stm)
+library(lubridate)
+library(reticulate)
+
+#### Read data ####
+hansard_corpus <- read_parquet("data/02-analysis_data/cleaned_data.parquet")
+
+
+# Filter by year (2020) and remove missing party values
+hansard_subset <- hansard_corpus %>%
+  filter(year == 2020) %>%   # Select only 2020 speeches
+  filter(!is.na(party)) %>%  # Remove rows where `party` is NA
+  select(name, body, gender, party)  # Keep only relevant columns
+
+# Ensure text is character format
+hansard_subset$body <- as.character(hansard_subset$body)
+
+# Remove empty speeches
+hansard_subset <- hansard_subset[nchar(hansard_subset$body) > 0, ]
+
+# Check final dataset size
+cat("Final rows in hansard_subset:", nrow(hansard_subset), "\n")
+
+
+# Convert text column to character format
+hansard_subset$body <- as.character(hansard_subset$body)
+
+# Create a corpus from the filtered dataset
+hansard_corpus <- corpus(hansard_subset, text_field = "body")
+
+# Ensure sizes match before tokenization
+cat("Rows in hansard_subset:", nrow(hansard_subset), "\n")
+cat("Texts in corpus:", length(as.character(hansard_corpus)), "\n")
+
+# Tokenization
+hansard_tokens <- tokens(hansard_corpus, remove_punct = TRUE, remove_numbers = TRUE) %>%
+  tokens_remove(stopwords("en"))
+
+# Create document-feature matrix (DFM)
+dfm_hansard <- dfm(hansard_tokens)
+
+# Check document count in the matrix
+cat("Documents in dfm_hansard:", nrow(dfm_hansard), "\n")
+
+# Identify non-empty documents
+valid_docs <- rowSums(dfm_hansard) > 0  # TRUE for valid, FALSE for empty
+
+# Apply filtering to both `dfm_hansard` and `hansard_subset`
+dfm_hansard <- dfm_hansard[valid_docs, ]
[…]

### 2025-02-07 scripts/06-stm.R
fix comments

@@ -86,6 +86,7 @@ saveRDS(stm_model, file = "models/hansard_topics.rda")
 
 
 
+# BERTopic 
 
 bertopic <- import("bertopic")
 # Ensure 'body' column is character format
@@ -108,12 +109,14 @@ saveRDS(topic_model, file = "models/bertopic_model.rds")
 
 
 
+# Create hansard subset dataset 
+
 hansard_subset <- hansard_corpus %>%
   filter(year == 2020) %>%
   filter(!is.na(party)) %>%
   filter(!is.na(gender)) %>%
   filter(body != "")  # Remove empty speeches
 
-
+# Save hansard subset
 saveRDS(hansard_subset, file = here::here("models/hansard_subset.rds"))
 

### 2025-02-28 paper/paper.qmd
more stm

--- 2025-01-24 paper/paper.qmd
@@
 
-```
-
-```{r}
-#| include: false
-#| warning: false
-#| message: false
-hansard_corpus <- read_parquet(here::here("data/02-analysis_data/cleaned_data.parquet"))
-```
-
-```{r}
-#| include: false
+library(stm)
+library(quanteda)
+library(tm)
+```
+
+```{r}
+#| include: false
+#| warning: false
+#| message: false
+hansard_corpus <- read_parquet(here::here("C:/Users/35911/Downloads/Hansard_Interruptions/data/02-analysis_data/cleaned_data.parquet"))
+
+```
+
+```{r}
 #| warning: false
@@
 # View the first few rows
-head(hansard_corpus, 150)
+#head(hansard_corpus, 150)
 
@@
 
-@tbl-ingov1, @tbl-ingov2, and @fig-gov offer a detailed look at interruptions during parliamentary sessions, categorized by members' government status and gender.
+@tbl-ingov1 and @fig-gov offer a detailed look at interruptions during parliamentary sessions, categorized by members' government status and gender.
 Notably, interruptions are extremely rare for members with clearly identified status.
@@
 # Print the resulting dataset to verify
-print(interruptions_question_analysis)
+#print(interruptions_question_analysis)
 
@@
 # Print the resulting dataset to verify
-print(interruptions_question_analysis)
+#print(interruptions_question_analysis)
 ```
@@
 # Print the data to see the word counts
-head(hansard_corpus1)
+#head(hansard_corpus1)
 ```
@@
   labs(
-    title = "Density Distribution of Word Count by Gender (Word Count ≤ 500)",
+    title = "Density Distribution of Word Count by Gender (Word Count < 500)",
     x = "Word Count",
@@
 model1 <-
-  readRDS(file = here::here("models/model1.rds"))
+  readRDS(file = here::here("C:/Users/35911/Downloads/Hansard_Interruptions/models/model1.rds"))
 
@@
 model2 <-
-  readRDS(file = here::here("models/model2.rds"))
+  readRDS(file = here::here("C:/Users/35911/Downloads/Hansard_Interruptions/models/model2.rds"))
 
@@
 
+```{r}
+#| include: false
+#| eval: true
+#| warning: false
+#| message: false
+hansard_topics <- readRDS(file = here::here("C:/Users/35911/Downloads/Hansard_Interruptions/models/hansard_topics.rda"))
+```
+
+```{r}
+#| include: false
+#| warning: false
+labelTopics(hansard_topics)
+```
+
+To analyze discussions in the Australian Parliament, I applied Structural Topic Modeling (STM) to identify key themes in speeches from 2020.
+The process began with data preprocessing, where I filtered the dataset to include only relevant entries, removed missing values, and structured the text data for analysis.
+A document-feature matrix (DFM) was then created, representing word frequencies while eliminating punctuation, stopwords, and low-frequency terms to improve model efficiency.
+
+The STM model was trained with 10 topics and incorporated party affiliation and speaker gender as prevalence covariates, allowing for an examination of how these factors influence topic distribution.
+The model was optimized over 50 iterations, ensuring convergence and stability.
+The final output provided a breakdown of the dominant topics, with key terms extracted using highest probability words, FREX words (distinctive to each topic), Lift words (rare but highly relevant), and Score words (best summarizing a topic’s meaning).
+
+```{r, fig.width=10, fig.height=6}
+#| echo: false
+#| eval: true
+#| label: tbl-stm_prop
+#| tbl-cap: "STM Topic Proportion Plot "
+#| warning: false
+plot(hansard_topics, type = "summary", n = 5)
+```
+
+@tbl-stm_prop provides an overview of the most prevalent themes in the 2020 Australian parliamentary speeches.
+The x-axis represents the expected topic proportions, indicating how frequently each topic appears across the dataset.
+The y-axis lists the top topics, summarized by their most representative words.
+
+From this visualization, Topic 5 ("minister, government, time, just") emerges as the most dominant theme, suggesting that government policies, ministerial discussions, and legislative matters were central to parliamentary discourse.
+Topic 8 ("people, government, need, now") follows closely, highlighting debates around public needs, government interventions, and social policies.
+Other significant topics include healthcare (Topic 10), economic measures (Topic 4), legal and family-related issues (Topic 7), and national security (Topic 1).
+
+The distribution of topics provides insights into policy priorities and legislative focus areas during 2020.
+By incorporating metadata such as speaker affiliation and gender, further analysis can uncover how different political groups or demographics engaged with these key issues.
+
+```{r}
+#| include: false
+library(stm)
+library(dplyr)
+library(readr)
+
+# Define years and create empty list for storage
+years <- 1998:2022
+topic_props_list <- list()
+
+# Loop through each year and extract topic proportions & keywords
+for (year in years) {
+  model_path <- paste0("C:/Users/35911/Downloads/Hansard_Interruptions/models/hansard_topics_", year, ".rda")
+
+  if (file.exists(model_path)) {
+    stm_model <- readRDS(model_path)
+
+    # Extract topic proportions
+    topic_props <- data.frame(
+      Year = year,
+      Topic = paste0("Topic_", 1:ncol(stm_model$theta)),  # STM topics
+      Proportion = colMeans(stm_model$theta)  # Average topic proportion
+    )
+
+    # Extract top words for each topic
+    topic_labels <- labelTopics(stm_model, n = 10)$prob  # Adjust 'n' for more words
+    topic_keywords <- apply(topic_labels, 1, paste, collapse = ", ")  # Convert to string
+
+    # Add keywords to dataframe
+    topic_props$Keywords <- topic_keywords
+
+    # Store results
+    topic_props_list[[as.character(year)]] <- topic_props
+  } else {
+    print(paste("Skipping", year, "- No Model Found"))
+  }
+}
+
+# Combine results into one dataframe
+topic_summary <- bind_rows(topic_props_list)
+
+# Save extracted topics & keywords
+write_csv(topic_summary, "topic_summary_1998_2022.csv")
+
+# View first few rows
+#print(topic_summary)
+
+```
+```{r}
+#| include: false
+library(dplyr)
+library(tidyr)
+library(readr)
+
+# Select the most prominent topic per year
+top_topics_per_year <- topic_summary %>%
+  group_by(Year) %>%
+  summarise(Top_Topic = first(Topic), Keywords = first(Keywords))  # First topic listed is the most prominent
+
+# Display table
+#print(top_topics_per_year)
+
+```
+
+```{r}
+#| echo: false
+#| eval: true
+#| label: tbl-prom_topic
+#| tbl-cap: "Most Prominent Topics Per Year"
+#| warning: false
+
+library(gt)
+
+# Create a nicely formatted table without the "Top Topic" column
+top_topics_per_year %>%
+  select(-Top_Topic) %>%  # Remove "Top Topic" column
+  gt() %>%
+  tab_header(
+    title = "Most Prominent Topics Per Year",
+    subtitle = "Extracted from Parliamentary Speeches (1998-2022)"
+  ) %>%
+  cols_label(
+    Year = "Year",
+    Keywords = "Representative Keywords"
+  ) %>%
+  fmt_markdown(columns = Keywords) %>%
+  tab_options(
+    table.font.size = "small",
+    heading.title.font.size = "large",
+    heading.subtitle.font.size = "medium"
+  )
+
+```
+
+To analyze the evolution of parliamentary discourse over time, I ran the Structural Topic Model (STM) on each year from 1998 to 2022, extracting the most prominent topics discussed in Australian parliamentary speeches annually.
+This approach allows us to track changes in political priorities and public policy discussions across different governments and time periods.
+
+@tbl-prom_topic that extracted topics from Australian parliamentary speeches from 1998 to 2022 reveal recurring themes in economic policy, governance, and public welfare.
+In 1998, keywords such as "funding, economy, billion, jobs, growth" indicate a strong focus on financial matters, possibly reflecting the economic policies of the Howard government.
+By 1999, discussions shifted toward legislative processes, with terms like "committee, country, parliament, act, bill, interest", suggesting an emphasis on governance and parliamentary procedures.
+
+In the early 2000s, taxation and economic regulation became central themes.
+The year 2000 prominently features "tax, GST, regional, cost", likely indicating debates around the introduction of the Goods and Services Tax (GST), a major economic reform at the time.
+By 2001, discussions expanded to include "question, education, state, leader, speaker", showing parliamentary focus on education policy and leadership discussions.
+The presence of "security, report, speaker" in later years, such as 2007, suggests increasing discussions about national security and legislative oversight.
+
+The financial crisis of 2008 appears to have influenced parliamentary discussions, as evidenced by the prominence of "government, economic, parliament, working" in that year.
+This aligns with government efforts to stabilize the economy and implement stimulus measures.
+By 2010, speeches featured "policy, education, billion, services", indicating continued investment in education and public services.
+In 2015, "education, students, infrastructure, training, funding" suggests an ongoing emphasis on higher education and workforce development.
+
+More recently, parliamentary discussions reflected the impact of the COVID-19 pandemic.
+In 2020, "government, security, legislation, parliament" emerged as dominant themes, which likely relate to emergency public health measures and pandemic response policies.
+By 2021 and 2022, terms such as "community, health, local, member" indicate a growing focus on public health, social support, and government intervention in economic recovery.
+
+Overall, this analysis provides a clear trajectory of parliamentary priorities over time.
+While early discussions centered on economic policy and legislative procedures, later years saw a growing emphasis on education, national security, and, more recently, public health.
+The keywords extracted from parliamentary speeches highlight shifting political and policy concerns, aligning with major national and global events during this period.
+```{r}
+#| include: false
+# Load necessary libraries
+library(dplyr)
+library(ggplot2)
+library(readr)
+
+topic_spikes <- topic_summary %>%
+  arrange(Topic, Year) %>%
+  group_by(Topic) %>%
+  mutate(Change = Proportion - lag(Proportion)) %>%
+  filter(!is.na(Change))  # Remove first year (no previous comparison)
+
+# Ensure unique topic-year-keyword mapping
+topic_spikes <- topic_spikes %>%
+  left_join(topic_summary %>% select(Year, Topic, Keywords), by = c("Year", "Topic")) %>%
+  distinct() %>%
+  select(-Keywords.x) %>%
+  rename(Keywords = Keywords.y)
+
+# Verify that Keywords exist
+print(head(topic_spikes))
+
+```
+
+```{r}
+#| echo: false
+#| eval: true
+#| label: fig-keytopics
+#| fig-cap: "Mentions of Key Topics Over Time"
+#| warning: false
+library(stringr)
+library(RColorBrewer)  # Better color schemes
+
+# Define keywords of interest
+keywords_of_interest <- c("education", "health", "economy", "policy", "tax", "energy")
+
+# Extract individual keyword counts separately
+tracked_topics <- topic_summary %>%
+  mutate(Cleaned_Keywords = str_extract_all(Keywords, paste(keywords_of_interest, collapse = "|"))) %>%
+  unnest(Cleaned_Keywords) %>%  # This separates each keyword into its own row
+  filter(Cleaned_Keywords != "") %>%
+  group_by(Year, Cleaned_Keywords) %>%
+  summarise(Count = sum(Proportion * 1000), .groups = "drop")  # Count each separately
+
+# Define color palette (use distinct colors)
+color_palette <- brewer.pal(n = length(unique(tracked_topics$Cleaned_Keywords)), name = "Dark2")
+
+# Plot evolution over time with improved colors
+ggplot(tracked_topics, aes(x = Year, y = Count, color = Cleaned_Keywords, group = Cleaned_Keywords)) +
+  geom_line(size = 1.2) +
+  geom_point(size = 2) +
+  scale_color_manual(values = color_palette) +  # Apply better colors
+  labs(title = "Mentions of Key Topics Over Time",
+       x = "Year",
+       y = "Count of Mentions",
+       color = "Topic Keywords") +
+  theme_minimal() +
+  theme(legend.position = "right", legend.text = element_text(size = 12))  # Improve legend readability
+
+```
+@fig-keytopics tracks the mentions of key policy topics—economy, education, energy, health, policy, and tax—in Australian parliamentary speeches from 1998 to 2022.
+Each topic fluctuates over time, reflecting shifts in legislative focus due to major events.
+
+Economic discussions remain stable but rise post-2008, aligning with the global financial crisis.
+Tax mentions spike around 2000, likely due to the introduction of the GST, and reappear during key economic reforms.
+Health surges in 2020, reflecting COVID-19 discussions, while education remains consistently relevant, peaking during policy changes in higher education and funding.
+Energy mentions rise after 2010, coinciding with climate policy debates like the carbon tax (2012-2014).
+The steady increase in policy discussions suggests a growing focus on governance and regulatory matters.
+These trends highlight how parliamentary attention shifts in response to national and global developments such as economic crises, education reforms, climate policies, and the pandemic.
+
 ### Model justification

### 2025-02-28 scripts/06-stm.R

@@ -84,6 +84,19 @@ saveRDS(stm_model, file = "models/hansard_topics.rda")
 
 
 
+# Create hansard subset dataset 
+
+hansard_subset <- hansard_corpus %>%
+  filter(year == 2020) %>%
+  filter(!is.na(party)) %>%
+  filter(!is.na(gender)) %>%
+  filter(body != "")  # Remove empty speeches
+
+# Save hansard subset
+saveRDS(hansard_subset, file = here::here("C:/Users/35911/Downloads/Hansard_Interruptions/models/hansard_subset.rds"))
+
+
+
 
 
 # BERTopic 
@@ -104,19 +117,66 @@ topics <- results[[1]]  # First value: Topic assignments
 probs <- results[[2]]   # Second value: Topic probabilities
 
 
+
 # Save the full BERTopic model
 saveRDS(topic_model, file = "models/bertopic_model.rds")
 
 
 
-# Create hansard subset dataset 
 
-hansard_subset <- hansard_corpus %>%
-  filter(year == 2020) %>%
-  filter(!is.na(party)) %>%
-  filter(!is.na(gender)) %>%
-  filter(body != "")  # Remove empty speeches
 
-# Save hansard subset
-saveRDS(hansard_subset, file = here::here("models/hansard_subset.rds"))
+#### Read full dataset ####
+hansard_corpus <- read_parquet("data/02-analysis_data/cleaned_data.parquet")
+
+# Define years to loop through
+years <- unique(hansard_corpus$year)  # Get all available years
+
+# Loop over each year
+for (yr in years) {
+  
+  cat("Processing Year:", yr, "\n")  # Print progress
+  
+  # Filter speeches for the specific year
+  hansard_subset <- hansard_corpus %>%
+    filter(year == yr) %>%   
+    filter(!is.na(party)) %>%  
+    select(name, body, gender, party)  
+  
+  # Ensure text is character format
+  hansard_subset$body <- as.character(hansard_subset$body)
+  
+  # Remove empty speeches
+  hansard_subset <- hansard_subset[nchar(hansard_subset$body) > 0, ]
+  
+  # Create a corpus
+  hansard_corpus_year <- corpus(hansard_subset, text_field = "body")
+  
+  # Tokenization
+  hansard_tokens <- tokens(hansard_corpus_year, remove_punct = TRUE, remove_numbers = TRUE) %>%
+    tokens_remove(stopwords("en"))
+  
+  # Create document-feature matrix (DFM)
[…]

### 2025-03-27 paper/paper.qmd
cleaning up

@@
 
-Although interjections are officially prohibited during a member's speech in the Australian Parliament, interruptions still occur frequently, particularly during heated debates often fueled by political disagreements [@aphInterruptions2025].
-This raises crucial questions about gender dynamics within the context of parliamentary debates in Australia.
-Concerns are growing regarding whether women are disproportionately interrupted compared to men, highlighting potential underlying biases that could influence the effectiveness and fairness of parliamentary proceedings.
+Interruptions are a defining feature of political discourse, often shaping the dynamics of power and influence within legislative bodies.
+While parliamentary rules in Australia officially prohibit interjections, disruptions remain a common occurrence, particularly in contentious debates where political tensions run high [@aphInterruptions2025].
+Beyond their immediate impact on debate flow, interruptions may reflect deeper systemic biases, particularly in relation to gender.
+If women in Parliament are interrupted more frequently than their male colleagues, this pattern could signal broader inequalities in political representation and influence, warranting closer examination.
 
@@
 
-Building on existing literature suggesting that the Australian High Court may exhibit better gender dynamics than its counterparts in the US, we aim to delve deeper into the issue of gender-based interruptions within the Australian Parliament.
-Utilizing the Australian Hansard, the official written record of parliamentary debates which has been digitized by Lindsay Katz and Rohan Alexander, we have access to comprehensive records of all parliamentary proceedings from 1998 to 2022 [@katz2023digitization].
-From the dataset, we aim to analyze the frequency and context of interruptions based on gender.
-Specifically, our study will focus on comparing the rates at which male and female parliamentarians are interrupted during their speeches.
+Building on these findings, our study investigates gender-based interruptions in the Australian Parliament using the Australian Hansard, the official written record of parliamentary proceedings digitized by Lindsay Katz and Rohan Alexander [@katz2023digitization].
+We first analyze the frequency and patterns of interruptions directed at male and female parliamentarians to assess whether gender influences how often speakers are interrupted.
+Beyond interruptions, we extend our analysis by examining the topics discussed in Parliament each year using Structural Topic Modeling (STM).
+This allows us to explore whether certain policy areas are associated with higher interruption rates and whether women engage in different policy discussions than men.
+By connecting these two aspects, we aim to identify whether interruptions are more prevalent in specific years and whether they coincide with particular topics, shedding light on how gender and discourse shape parliamentary debate.
 
 The remainder of this paper is structured as follows: @sec-data demonstrates the data used for this paper, @sec-model describes, justifies, and explains my model, @sec-results highlights the results of the predictions using tables and graphs, and @sec-discussion contains important implications and conclusions based on the findings.
+
+```{r}
+library(tinytex)
+
+#install.packages("tinytex")
+#tinytex::install_tinytex()
+
+#tinytex::tlmgr_update()
+#tinytex::tlmgr_install("latex-bin")
+#tinytex::tlmgr_install("xetex")
+
+#.libPaths()  # Check all library paths
+#find.package("rlang")  # Identify where the old version is installed
+```
+
+xelatex --version
 
@@
 library(stringr)
-
 library(stm)
@@
 #head(hansard_corpus, 150)
-
-```
-
-```{r}
-#| include: false
-#| warning: false
-#| message: false
 summary(hansard_corpus)
-
 ```
@@
 ## Data Cleaning
+To ensure consistency and accuracy in the analysis, we performed several data cleaning steps on the Hansard corpus dataset.
+One of the primary tasks was standardizing categorical variables, correcting data types, and filtering the dataset to focus on relevant parliamentary debates.
+
+First, we standardized the gender variable by converting it to a character type and addressing missing values.
+Any NA or empty string entries were replaced with "Unknown", ensuring that all observations were categorized as "Male", "Female", or "Unknown".
+Next, we processed the interjection (interject) variable, which indicates whether a speech was interrupted.
+Since it was originally stored as a mix of character and numeric values, we converted it into a numeric format while preserving any missing values.
+Similarly, the date column was transformed into a proper Date format (YYYY-MM-DD), and we extracted the year variable for longitudinal analysis.
+
+A critical filtering step was applied to retain only chamber speeches (fedchamb_flag == 0).
+This decision was made because chamber debates represent formal parliamentary discussions, including legislative debates and question periods, where interruptions carry significant political and procedural weight.
+In contrast, committee hearings and other non-chamber sessions often have different procedural norms and may not exhibit the same interruption patterns.
+Focusing on chamber data ensures that our findings reflect structured parliamentary interactions rather than informal or committee-based discussions.
+
+Additionally, we computed the word count for each speech by applying a regular expression that counts the number of words in the speech text (body).
+This provides insights into the length of speeches, which may be relevant in later analyses.
+
+@preview_cleaned provides a snapshot of key variables, including year, gender, interject, party, and word_count, allowing us to inspect how the dataset is structured post-cleaning.
+@sum_stats presents aggregated counts of speeches by gender, interruption status, and party affiliation.
+It highlights the number of speeches given by male and female parliamentarians, how often interruptions occur, and the distribution of party representation.
+Missing values are explicitly recorded where relevant.
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| tbl-cap: "Preview of the Cleaned Hansard Dataset"
+#| label: tbl-preview_cleaned
+# Select important variables for preview
+preview_table <- hansard_corpus %>%
+  select(year, gender, interject, party, word_count, fedchamb_flag) %>%
+  head(6)  # Show only the first 6 rows
+
+# Display the preview table
+kable(preview_table)
+
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| tbl-cap: "Summary Statistics of the Cleaned Hansard Dataset"
+#| label: tbl-sum_stats
+# Create a structured summary table
+summary_table <- data.frame(
+  Variable = c(
+    "Gender", "Gender", "Gender",
+    "Interject", "Interject",
+    "Party", "Party", "Party", "Party", "Party"
+  ),
+  Category = c(
+    "Male", "Female", "Unknown",
+    "No", "Yes",
+    "ALP", "LP", "Nats", "Other", "Missing"
+  ),
+  Count = c(
+    sum(hansard_corpus$gender == "Male", na.rm = TRUE),
+    sum(hansard_corpus$gender == "Female", na.rm = TRUE),
+    sum(hansard_corpus$gender == "Unknown", na.rm = TRUE),
+
+    sum(hansard_corpus$interject == 0, na.rm = TRUE),
+    sum(hansard_corpus$interject == 1, na.rm = TRUE),
+
+    sum(hansard_corpus$party == "ALP", na.rm = TRUE),
+    sum(hansard_corpus$party == "LP", na.rm = TRUE),
+    sum(hansard_corpus$party == "Nats", na.rm = TRUE),
+    sum(!hansard_corpus$party %in% c("ALP", "LP", "Nats") & !is.na(hansard_corpus$party)),
+    sum(is.na(hansard_corpus$party))
+  )
+)
+
+# Display the table in LaTeX-style format
+kable(summary_table)
+
+```
+
+By ensuring data consistency and filtering for relevant parliamentary discourse, these preprocessing steps provide a clean and structured dataset, ready for further analysis on gender-based interruptions and topic modeling in Australian parliamentary debates.
 
@@
 ```{r}
-#| echo: false
-#| warning: false
-#| message: false
-#| tbl-cap: "Gender Interruption Proportions Annual Comparison"
-#| label: tbl-compareyear
-
-# Prepare the data
-comparison_data <- final_data1 %>%
-  pivot_wider(
-    id_cols = year,
-    names_from = gender,
-    values_from = interruption_proportion
-  ) %>%
-  mutate(
-    More_Interrupted_Gender = case_when(
-      Male > Female ~ "Male",
-      Female > Male ~ "Female",
-      TRUE ~ "Equal"  # This handles cases where the interruption proportions are the same
-    )
-  )
-
-# Generate the table using gt
-comparison_data %>%
-  select(year, More_Interrupted_Gender) %>%  # Include only year and the gender comparison
-  gt() %>%
-  cols_label(
-    year = "Year",
-    More_Interrupted_Gender = "More Interrupted Gender"
-  ) %>%
-  tab_style(
-    style = cell_text(align = "left"),  # Align text to the left
-    locations = cells_body(columns = everything())  # Apply to all columns in the body
-  )
-
-```
-
-@tbl-compareyear displays the more interrupted gender every year in the parliament and compares all members and only chamber members.
-While most years are the same, there is a notable shift in the gender experiencing more frequent interruptions from 2018 to 2020.
-In the broader dataset, males were more frequently interrupted; however, this pattern shifts in the non-federal chamber data, where females became the more interrupted gender during these years.
-This change highlights the variability in gender dynamics within different parliamentary environments and suggests that factors specific to non-federal chamber settings may influence these interaction patterns more significantly for female members.
-
-```{r}
 #| include: false
@@
 print(interruptions_question_analysis)
-
+library(tinytex)
+library("xfun")
 ```
@@
   plot_annotation(
-    title = "Interruptions in Major Australian Political Parties by Gender",
     theme = theme(
@@
   labs(
-    title = "Interruptions Count by Government Status and Gender",
     x = "Government Status",
@@
   labs(
-    title = "Histogram of Word Counts in Speeches",
     x = "Word Count",
@@
 #| label: fig-density
-#| fig-cap: "Density Distribution of Word Count by Gender"
+#| fig-cap: "Density Distribution of Word Count by Gender (Word Count < 500)"
 # Filter the data to include only speeches with word counts under 500 and valid gender values
@@
   labs(
-    title = "Density Distribution of Word Count by Gender (Word Count < 500)",
     x = "Word Count",
@@
 
+In this model, \( y_i \) represents the binary outcome variable indicating whether a speech was interrupted (\(\text{interject} = 1\)) or not (\(\text{interject} = 0\)).
+The probability of an interruption (\(\pi_i\)) is modeled using a logistic link function, where the log-odds of an interruption are expressed as a linear combination of the intercept (\(\alpha\)) and the predictor variables: where \(\beta_1, \beta_2, \beta_3, \beta_4\) are the regression coefficients corresponding to each predictor.
+The variables included in the model are defined as follows: \(\text{gender}_i\) represents the speaker’s gender (Male, Female, or Unknown), \(\text{party}_i\) indicates the political party affiliation, \(\text{word\_count}_i\) captures the total number of words spoken in a given speech, and \(\text{word\_count\_gender}_i\) represents the interaction between word count and gender.
+
+To regularize the model and incorporate prior information, we assign informative normal priors to the intercept and coefficients.
+Specifically, the intercept \(\alpha\) follows a normal distribution with a mean of 0 and a standard deviation of 5, while the coefficients \(\beta_1, \beta_2, \beta_3,\) and \(\beta_4\) follow normal distributions with a mean of 0 and a standard deviation of 2.5.
+These priors help stabilize the estimates, particularly in cases where the data might be sparse or imbalanced.
+
+This modeling approach is chosen for several reasons. Firstly, logistic regression is well-suited
+for binary outcome variables, making it appropriate for interruption probabilities.
+Additionally, Bayesian logistic regression is particularly well-suited for this analysis because it accommodates uncertainty in parameter estimates and allows for the incorporation of prior knowledge.
+Bayesian methods are advantageous in addressing potential multicollinearity and producing interpretable probabilistic estimates.
+
+The model was implemented in R using the `rstanarm` package [@rstanarm], which applies Markov chain Monte Carlo (MCMC) sampling to estimate the posterior distributions of the model parameters.
+To optimize computational efficiency, I randomly sampled 1000 observations for model fitting, ensuring a balance between computational feasibility and statistical reliability.
+
 # Results {#sec-results}
@@
   readRDS(file = here::here("C:/Users/35911/Downloads/Hansard_Interruptions/models/model1.rds"))
+
+tinytex::tinytex_root()
 
@@
 These findings underscore the combined effects of gender, party dynamics, and speech characteristics in shaping interruption patterns.
+
+Model diagnostics, including convergence checks and posterior summaries, and explanations can be found in @Appendix
 
@@
 #| message: false
-model2 <-
-  readRDS(file = here::here("C:/Users/35911/Downloads/Hansard_Interruptions/models/model2.rds"))
-
-```
-
-```{r}
-#| echo: false
-#| eval: true
-#| label: tbl-modelresults2
-#| tbl-cap: "Model 2 for Interruptions (n = 1000)"
-#| warning: false
-
-modelsummary(
-  list(
-    "Speech Interrupted" = model2
-  ),
-  statistic = "mad"
-  )
-```
-
-The logistic regression model @tbl-modelresults2 continues to highlight key predictors of interruptions during speeches, with the removal of party.
-Male speakers remain more likely to experience interruptions than female speakers, but the effect size has slightly decreased, reflecting a smaller increase in the likelihood of interruptions.
-The relationship between speech length and interruptions remains consistent, with longer speeches slightly reducing the likelihood of interruptions.
-The interaction between word count and gender also remains unchanged, suggesting that longer speeches by male speakers are still slightly more likely to invite interruptions compared to those by females.
-
-```{r}
-#| include: false
-#| eval: true
-#| warning: false
-#| message: false
 hansard_topics <- readRDS(file = here::here("C:/Users/35911/Downloads/Hansard_Interruptions/models/hansard_topics.rda"))
@@
 
-To analyze discussions in the Australian Parliament, I applied Structural Topic Modeling (STM) to identify key themes in speeches from 2020.
+The Bayesian logistic regression model quantifies gender-based interruptions in the Australian Parliament, assessing whether female speakers face disproportionately more interjections than their male counterparts.
+However, interruptions alone do not fully capture discourse dynamics.
+To further explore these patterns, I applied Structural Topic Modeling (STM) to identify the most discussed topics in parliamentary speeches, incorporating gender and party affiliation as prevalence covariates to examine how different groups engage with various topics.
+
+By linking the most discussed topics in a given year to the most interrupted gender, I aim to determine whether interruptions are associated with particular types of discourse.
+For example, if female parliamentarians experienced the highest interruption rates in 2020, I will compare this with the dominant topics that year to uncover potential gendered patterns.
+This dual approach—quantifying interruptions through regression and analyzing speech content through topic modeling—offers deeper insight into both who gets interrupted and what is being discussed when those interruptions occur.
+
 The process began with data preprocessing, where I filtered the dataset to include only relevant entries, removed missing values, and structured the text data for analysis.
 A document-feature matrix (DFM) was then created, representing word frequencies while eliminating punctuation, stopwords, and low-frequency terms to improve model efficiency.
-
 The STM model was trained with 10 topics and incorporated party affiliation and speaker gender as prevalence covariates, allowing for an examination of how these factors influence topic distribution.
@@
 The final output provided a breakdown of the dominant topics, with key terms extracted using highest probability words, FREX words (distinctive to each topic), Lift words (rare but highly relevant), and Score words (best summarizing a topic’s meaning).
-
-```{r, fig.width=10, fig.height=6}
-#| echo: false
-#| eval: true
-#| label: tbl-stm_prop
-#| tbl-cap: "STM Topic Proportion Plot "
-#| warning: false
-plot(hansard_topics, type = "summary", n = 5)
-```
-
-@tbl-stm_prop provides an overview of the most prevalent themes in the 2020 Australian parliamentary speeches.
-The x-axis represents the expected topic proportions, indicating how frequently each topic appears across the dataset.
-The y-axis lists the top topics, summarized by their most representative words.
-
-From this visualization, Topic 5 ("minister, government, time, just") emerges as the most dominant theme, suggesting that government policies, ministerial discussions, and legislative matters were central to parliamentary discourse.
-Topic 8 ("people, government, need, now") follows closely, highlighting debates around public needs, government interventions, and social policies.
-Other significant topics include healthcare (Topic 10), economic measures (Topic 4), legal and family-related issues (Topic 7), and national security (Topic 1).
-
-The distribution of topics provides insights into policy priorities and legislative focus areas during 2020.
-By incorporating metadata such as speaker affiliation and gender, further analysis can uncover how different political groups or demographics engaged with these key issues.
 
@@
 #| warning: false
-
-library(gt)
 
@@
   tab_header(
-    title = "Most Prominent Topics Per Year",
-    subtitle = "Extracted from Parliamentary Speeches (1998-2022)"
+    title = "Most Prominent Topics Per Year"
   ) %>%
@@
   scale_color_manual(values = color_palette) +  # Apply better colors
-  labs(title = "Mentions of Key Topics Over Time",
+  labs(
        x = "Year",
@@
   theme(legend.position = "right", legend.text = element_text(size = 12))  # Improve legend readability
+
+library(xfun)
 
@@
 
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| tbl-cap: "Gender Interruption Proportions Annual Comparison"
+#| label: tbl-compareyear
+
+# Prepare the data
+comparison_data <- final_data1 %>%
+  pivot_wider(
+    id_cols = year,
+    names_from = gender,
+    values_from = interruption_proportion
+  ) %>%
+  mutate(
+    More_Interrupted_Gender = case_when(
+      Male > Female ~ "Male",
+      Female > Male ~ "Female",
+      TRUE ~ "Equal"  # This handles cases where the interruption proportions are the same
+    )
+  )
+
+# Generate the table using gt
+comparison_data %>%
+  select(year, More_Interrupted_Gender) %>%  # Include only year and the gender comparison
+  gt() %>%
+  cols_label(
+    year = "Year",
+    More_Interrupted_Gender = "More Interrupted Gender"
+  ) %>%
+  tab_style(
+    style = cell_text(align = "left"),  # Align text to the left
+    locations = cells_body(columns = everything())  # Apply to all columns in the body
+  )
+
+```
+
+@tbl-compareyear displays the more interrupted gender every year in the parliament and compares all members and only chamber members.
+While most years are the same, there is a notable shift in the gender experiencing more frequent interruptions from 2018 to 2020.
+In the broader dataset, males were more frequently interrupted; however, this pattern shifts in the non-federal chamber data, where females became the more interrupted gender during these years.
+This change highlights the variability in gender dynamics within different parliamentary environments and suggests that factors specific to non-federal chamber settings may influence these interaction patterns more significantly for female members.
+
+The relationship between key discussion topics and gender-based interruptions in the Australian Parliament reveals interesting patterns over time.
+One notable observation is that years with significant shifts in dominant topics often correspond to changes in the most interrupted gender.
+For example, in 2001 and 2003–2007, when female parliamentarians faced more interruptions, discussions around education, policy, and health were prominent.
+This suggests that women may have been more vocal in policy-driven debates during these years, potentially contributing to higher interruption rates.
+Conversely, in years when male speakers were interrupted more often, such as 1998–2000, 2008–2013, and 2020–2022, the most discussed topics included economy, tax, and government policy, indicating that male parliamentarians may have taken the lead in these areas.
+
+Another striking trend is the spike in health-related discussions in 2020, which coincides with a shift back to male parliamentarians being more interrupted.
+This could reflect the heightened focus on COVID-19-related policies, with male politicians engaging in more contentious discussions.
+Similarly, 2018 and 2019 saw female parliamentarians experiencing the highest interruptions, aligning with rising debates on legislation and social policies—areas where women may have had greater involvement.
+
+Overall, these findings suggest that interruption patterns are not random but are influenced by the topics dominating parliamentary discourse each year.
+When discussions center on traditionally social or policy-oriented issues, women appear to face higher interruption rates, while economic and government-related debates tend to correspond with increased interruptions for male speakers.
+This interplay between gender, parliamentary discourse, and interruptions underscores how power dynamics in political speech are shaped by both who is speaking and what is being discussed.
+
 ### Model justification
 
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
+We expect a positive relationship between the= size of the wings and time spent aloft. In particular...
 
@@
 
+```{r}
+library(bayesplot)
+#mcmc_trace(as.array(model1))
+
+```
+
+```{r}
+#pp_check(model1, nsamples = 100)
+
+```
+
 # Additional data details

### 2025-03-27 scripts/06-stm.R

@@ -8,7 +8,7 @@
 # - 02-download_data.R must have been run
 # - 03-clean_data.R must have been run
 
-
++++
 #### Workspace setup ####
 library(tidyverse)
 library(quanteda)

### 2025-03-28 paper/paper.qmd
add appendix, more fixes

@@
 ```{r}
-library(tinytex)
+#| include: false
 
@@
 ```
-
-xelatex --version
 
@@
 library(tm)
+library(tinytex)
+library(bayesplot)
+
 ```
@@
 
-@preview_cleaned provides a snapshot of key variables, including year, gender, interject, party, and word_count, allowing us to inspect how the dataset is structured post-cleaning.
-@sum_stats presents aggregated counts of speeches by gender, interruption status, and party affiliation.
+@tbl-preview_cleaned provides a snapshot of key variables, including year, gender, interject, party, and word_count, allowing us to inspect how the dataset is structured post-cleaning.
+@tbl-sum_stats presents aggregated counts of speeches by gender, interruption status, and party affiliation.
 It highlights the number of speeches given by male and female parliamentarians, how often interruptions occur, and the distribution of party representation.
@@
 \end{align}
-
-In this model, \( y_i \) represents the binary outcome variable indicating whether a speech was interrupted (\(\text{interject} = 1\)) or not (\(\text{interject} = 0\)).
-The probability of an interruption (\(\pi_i\)) is modeled using a logistic link function, where the log-odds of an interruption are expressed as a linear combination of the intercept (\(\alpha\)) and the predictor variables: where \(\beta_1, \beta_2, \beta_3, \beta_4\) are the regression coefficients corresponding to each predictor.
-The variables included in the model are defined as follows: \(\text{gender}_i\) represents the speaker’s gender (Male, Female, or Unknown), \(\text{party}_i\) indicates the political party affiliation, \(\text{word\_count}_i\) captures the total number of words spoken in a given speech, and \(\text{word\_count\_gender}_i\) represents the interaction between word count and gender.
-
-To regularize the model and incorporate prior information, we assign informative normal priors to the intercept and coefficients.
-Specifically, the intercept \(\alpha\) follows a normal distribution with a mean of 0 and a standard deviation of 5, while the coefficients \(\beta_1, \beta_2, \beta_3,\) and \(\beta_4\) follow normal distributions with a mean of 0 and a standard deviation of 2.5.
-These priors help stabilize the estimates, particularly in cases where the data might be sparse or imbalanced.
+In this model, $y_i$ represents the binary outcome variable indicating whether a speech was interrupted ($\text{interject} = 1$) or not ($\text{interject} = 0$).
+The probability of an interruption ($\pi_i$) follows a logistic distribution:
+
+$\text{logit}(\pi_i) = \alpha + \beta_1 \times \text{gender}_i + \beta_2 \times \text{party}_i + \beta_3 \times \text{word\_count}_i + \beta_4 \times \text{word\_count\_gender}_i$
+
+where $\beta_1, \beta_2, \beta_3,$ and $\beta_4$ are the regression coefficients.
+The model includes the following predictors: $\text{gender}_i$ (Male, Female, or Unknown), $\text{party}_i$ (political party affiliation), $\text{word\_count}_i$ (total words spoken in a speech), and $\text{word\_count\_gender}_i$ (interaction between word count and gender).
+
+To regularize the model, we assign normal priors to the intercept and coefficients.
+The intercept $\alpha$ follows a normal distribution with mean 0 and standard deviation 5, while the coefficients $\beta_1, \beta_2, \beta_3,$ and $\beta_4$ follow normal distributions with mean 0 and standard deviation 2.5.
+These priors provide stability, especially when data is sparse or imbalanced.
 
@@
 To optimize computational efficiency, I randomly sampled 1000 observations for model fitting, ensuring a balance between computational feasibility and statistical reliability.
+
+## Model justification
+
+A relationship is expected between gender, party affiliation, and speech interruptions in parliamentary debates.
+Male speakers are likely to face more interruptions than female speakers, reflecting common patterns in political discourse.
+However, interruptions may still occur for female speakers depending on the context of their speech.
+
+For party affiliation, the ALP and LNP, as the two main parties, are expected to show different interruption patterns.
+ALP members may experience more interruptions, especially when in opposition, while LNP members may face fewer interruptions, particularly when in government.
+Other parties and independents may not follow a clear pattern due to their varying roles in debates.
+
+Speech length also matters—longer speeches may be interrupted less, possibly because they allow speakers to establish their points, while shorter speeches might invite more interjections.
+The interaction between word count and gender suggests that longer speeches by male speakers could attract more interruptions, while this trend may be weaker for female speakers.
+
+A Bayesian approach helps capture uncertainty in these patterns while ensuring stable estimates, even with imbalanced data.
+This method provides a clearer view of how gender, party, and speech characteristics influence interruptions in parliamentary debates.
 
@@
 @tbl-modelresults1 identifies key predictors including gender, party, and word count of speech interruptions in parliamentary proceedings.
-Gender plays an important role, with male speakers more likely to experience interruptions compared to female speakers.
+The intercept, which represents the baseline category in the model, corresponds to female speakers from the LP party.
+This suggests that all other coefficients should be interpreted as deviations from this baseline.Gender plays an important role, with male speakers more likely to experience interruptions compared to female speakers.
 This suggests that men face slightly higher odds of interjections during their speeches.
@@
 
-Model diagnostics, including convergence checks and posterior summaries, and explanations can be found in @Appendix
+Model diagnostics, including convergence checks and posterior summaries, and explanations can be found in Appendix @sec-model-details
 
@@
 
-### Model justification
-
-We expect a positive relationship between the= size of the wings and time spent aloft. In particular...
-
-We can use maths by including latex between dollar signs, for instance $\theta$.
-
 # Discussion {#sec-discussion}
@@
 
-```{r}
-library(bayesplot)
-#mcmc_trace(as.array(model1))
-
-```
-
-```{r}
-#pp_check(model1, nsamples = 100)
-
-```
-
-# Additional data details
-
 # Model details {#sec-model-details}
@@
 
-## Diagnostics
+```{r}
+#| label: fig-post_dist
+#| fig-cap: Posterior distribution
+#| echo: false
+#| warning: false
+#| message: false
+pp_check(model1, nsamples = 100) +
+  theme(legend.position = "bottom")
+
+```
+In @fig-post_dist, a posterior distribution is implemented.
+This compares the actual instances of speech interruptions with the predicted probabilities from the posterior distribution of the Bayesian logistic regression model.
+The close alignment between the posterior distribution and the observed data suggests that my model provides a strong representation of the factors influencing interruptions in parliamentary speech.
+
+## Markov chain Monte Carlo Convergence Check
+
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+#| label: fig-trace
+#| fig-cap: "Trace plot"
+#| fig.width: 12
+#| fig.height: 25   # Increased height for better spacing
+
+# Generate trace plot with better spacing
+trace_plot <- mcmc_trace(
+  as.array(model1),
+  facet_args = list(ncol = 2)  # Keep two plots per row
+) +
+  theme_minimal(base_size = 14) +  # Increase base text size
+  theme(
+    axis.text.x = element_text(size = 12),  
+    axis.text.y = element_text(size = 12),
+    strip.text = element_text(size = 14, face = "bold"),  
+    legend.text = element_text(size = 12),  
+    legend.title = element_text(size = 14),
+    panel.spacing.y = unit(2, "cm")  # **Increase vertical spacing**
+  )
+
+trace_plot
+
+```
+
+@fig-trace is the trace plot of the model. The lines are horizontal and oscillating, and have overlaps between the chains, suggesting no existing signs of issues with the model.
+
+```{r}
+#| echo: false
+#| eval: true
+#| message: false
+#| warning: false
+#| label: fig-rhat
+#| fig-cap: "Rhat plot"
+plot(model1, "rhat")
+
+```
+@fig-rhat is the Rhat plot of the model.
+It compares the variability within each chain to the variability between chains in MCMC.
+In ideal condition, the Rhat should be close to 1, indicating that the chains have converged to the same distribution.
+This Rhat plot is indeed close to 1, suggesting that the MCMC algorithm has reached convergence for the model.
+## Credibility Interval {#sec-credibility-interval}
+
+```{r}
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+#| label: fig-modelresults1
+#| fig-cap: "Credible intervals for predictors of interruptions"
+
+modelplot(model1, conf_level = 0.90, size = 0.2) +
+  labs(x = "90% credibility interval")
+
+```
+@fig-modelresults1 displays the 90% credibility intervals for the posterior distributions of the logistic regression model predicting interruptions in parliamentary speech.
+Each point represents the posterior mean, while the horizontal lines indicate the uncertainty in the estimates.
+
+Although many party coefficients include zero within their credibility intervals—suggesting they do not have a statistically significant effect—the ALP and LNP show meaningful effects.
+These two parties, the dominant political groups in Australia, have coefficients that suggest they significantly influence interruptions.
+LP is included in the intercept, meaning all other party estimates should be interpreted relative to this baseline category.
+
+Gender also plays a role in predicting interruptions.
+Both "Male" and "Female" categories show significant effects, while "Gender Unknown" does not, likely due to a smaller sample size.
+The strong effect for male speakers suggests that gender influences interjections, aligning with findings that men experience more interruptions in parliamentary debates.
+
+Additionally, word count has a noticeable effect.
+Longer speeches tend to be associated with fewer interruptions, implying that shorter speeches might invite more interjections.
+The interaction term between word count and gender suggests that male speakers might experience a slight increase in interruptions as speech length grows, whereas the effect is less pronounced for female speakers.
 

### 2025-03-28 paper/paper.qmd
discussions and others

@@
 
-## First discussion point {#sec-first-point}
-
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
-
-## Second discussion point
-
-Please don't use these as sub-heading labels - change them to be what your point actually is.
-
-## Third discussion point
-
-## Weaknesses and next steps
-
-Weaknesses and next steps should also be included.
+## Gender and Interruptions in the Australian Parliament
+
+Our analysis confirms that male parliamentarians experience more interruptions in absolute terms.
+However, after adjusting for differences in speech frequency, the gap between genders narrows significantly, with male and female MPs facing comparable rates of interruptions relative to their total speeches.
+This challenges the common assumption that female parliamentarians are disproportionately interrupted, at least in the Australian Parliament.
+While gender remains a factor in parliamentary discourse, its impact on interruptions appears less pronounced than in other legislative bodies, such as the U.S.
+Congress.
+
+Despite the lack of a large gender-based disparity in interruptions, there is evidence that interruptions affect speech length.
+On average, interrupted speeches are significantly shorter than uninterrupted ones.
+Female MPs, while generally delivering longer speeches than male MPs, experience a more pronounced drop in speech length when interrupted.
+This suggests that while men may be interrupted more often, interruptions may have a stronger effect on women's ability to maintain the floor.
+This aligns with previous studies suggesting that interruptions can serve as a subtle tool to limit participation.
+
+## The Role of Political Party and Government Status
+
+Political party affiliation plays a significant role in shaping interruption patterns.
+MPs from the Australian Labor Party (ALP) experience more interruptions than those from the Liberal Party (LP).
+This aligns with expectations, given the adversarial nature of parliamentary debate, where opposition parties face heightened scrutiny and interjections.
+Notably, interruptions are significantly less frequent for MPs in government, reinforcing the idea that institutional authority provides protection from speech disruptions.
+However, due to missing data on government status for many MPs, this result should be interpreted with caution.
+
+The structural topic model (STM) further reveals that interruptions are not randomly distributed but correlate with certain debate topics.
+Economic and tax-related discussions—often led by male MPs—coincide with higher male interruptions.
+In contrast, years where female MPs experienced more interruptions align with increased discussions on education, health, and social policy.
+This suggests that rather than gender alone determining interruption rates, the subject matter of the debate plays a role in shaping speech dynamics.
+MPs may be more likely to interrupt when they perceive a speaker as challenging their party’s position on key issues.
+
+## Temporal Trends and External Factors
+
+The temporal analysis highlights key shifts in interruption patterns over time.
+The proportion of interruptions peaked in the early 2010s before declining in recent years.
+This trend aligns with broader changes in parliamentary norms and debate structures, including reforms aimed at improving parliamentary decorum.
+Notably, the gendered patterns of interruptions fluctuated, with women experiencing higher relative interruption rates in some years (e.g., 2018–2019) but lower rates in others.
+This variability suggests that external political events, leadership changes, and shifts in parliamentary culture may influence interruption dynamics.
+
+## Limitations and Future Research Directions
+
+This study has several limitations that should be considered when interpreting the results.
+First, missing data on important variables such as government status prevents a complete analysis of how being in government versus opposition affects interruptions.
+While our results indicate that MPs in government experience fewer interruptions, this conclusion is weakened by the number of MPs whose status is not recorded.
+
+Second, our study is descriptive rather than causal.
+The analysis identifies associations between gender, party affiliation, debate topics, and interruptions, but it does not establish whether these factors directly cause changes in interruption rates.
+Other unmeasured variables, such as individual speaking styles, political seniority, or chamber dynamics, may influence interruptions.
+Future research could incorporate controlled experiments or natural experiments (e.g., rule changes in Parliament) to test causal mechanisms.
+
+Lastly, there is potential for reverse causality, particularly regarding speech length.
+While the results indicate that interruptions correlate with shorter speeches, it is unclear whether interruptions cause speakers to shorten their remarks or if shorter speeches are inherently more likely to be interrupted.
+A similar concern applies to gender-based differences in speech length—longer speeches by female MPs may attract interruptions, but interruptions may also lead to shorter contributions over time.
+Future research using longitudinal designs or speaker-level fixed effects models could help disentangle these relationships.
 

### 2025-03-28 paper/paper.qmd
abstract

@@
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "Interruptions shape parliamentary discourse, influencing power dynamics and legislative interactions.
+Using Hansard records from 1998 to 2022, this study applies Bayesian logistic regression and Structural Topic Modeling (STM) to examine how gender, party affiliation, and debate topics affect speech interruptions in the Australian Parliament.
+The analysis finds that while men experience more interruptions overall, differences between genders diminish when accounting for speech frequency, with political party and debate topics playing a larger role in determining interruption rates.
+These findings highlight the complex nature of parliamentary speech, emphasizing that interruptions are not solely gender-driven but are also shaped by institutional and political contexts."
 format: pdf
@@
 The model was implemented in R using the `rstanarm` package [@rstanarm], which applies Markov chain Monte Carlo (MCMC) sampling to estimate the posterior distributions of the model parameters.
-To optimize computational efficiency, I randomly sampled 1000 observations for model fitting, ensuring a balance between computational feasibility and statistical reliability.
+To optimize computational efficiency, we randomly sampled 1000 observations for model fitting, ensuring a balance between computational feasibility and statistical reliability.
 
@@
 
-A relationship is expected between gender, party affiliation, and speech interruptions in parliamentary debates.
 Male speakers are likely to face more interruptions than female speakers, reflecting common patterns in political discourse.
-However, interruptions may still occur for female speakers depending on the context of their speech.
-
-For party affiliation, the ALP and LNP, as the two main parties, are expected to show different interruption patterns.
+However, interruptions may still occur for female speakers depending on the context of their speech.For party affiliation, the ALP and LNP, as the two main parties, are expected to show different interruption patterns.
 ALP members may experience more interruptions, especially when in opposition, while LNP members may face fewer interruptions, particularly when in government.
@@
 The intercept, which represents the baseline category in the model, corresponds to female speakers from the LP party.
-This suggests that all other coefficients should be interpreted as deviations from this baseline.Gender plays an important role, with male speakers more likely to experience interruptions compared to female speakers.
+This suggests that all other coefficients should be interpreted as deviations from this baseline.
+Gender plays an important role, with male speakers more likely to experience interruptions compared to female speakers.
 This suggests that men face slightly higher odds of interjections during their speeches.
@@
 However, interruptions alone do not fully capture discourse dynamics.
-To further explore these patterns, I applied Structural Topic Modeling (STM) to identify the most discussed topics in parliamentary speeches, incorporating gender and party affiliation as prevalence covariates to examine how different groups engage with various topics.
-
-By linking the most discussed topics in a given year to the most interrupted gender, I aim to determine whether interruptions are associated with particular types of discourse.
-For example, if female parliamentarians experienced the highest interruption rates in 2020, I will compare this with the dominant topics that year to uncover potential gendered patterns.
+To further explore these patterns, we applied Structural Topic Modeling (STM) to identify the most discussed topics in parliamentary speeches, incorporating gender and party affiliation as prevalence covariates to examine how different groups engage with various topics.
+
+By linking the most discussed topics in a given year to the most interrupted gender, we aim to determine whether interruptions are associated with particular types of discourse.
+For example, if female parliamentarians experienced the highest interruption rates in 2020, we will compare this with the dominant topics that year to uncover potential gendered patterns.
 This dual approach—quantifying interruptions through regression and analyzing speech content through topic modeling—offers deeper insight into both who gets interrupted and what is being discussed when those interruptions occur.
 
-The process began with data preprocessing, where I filtered the dataset to include only relevant entries, removed missing values, and structured the text data for analysis.
+The process began with data preprocessing, where we filtered the dataset to include only relevant entries, removed missing values, and structured the text data for analysis.
 A document-feature matrix (DFM) was then created, representing word frequencies while eliminating punctuation, stopwords, and low-frequency terms to improve model efficiency.
@@
 
-To analyze the evolution of parliamentary discourse over time, I ran the Structural Topic Model (STM) on each year from 1998 to 2022, extracting the most prominent topics discussed in Australian parliamentary speeches annually.
+To analyze the evolution of parliamentary discourse over time, we ran the Structural Topic Model (STM) on each year from 1998 to 2022, extracting the most prominent topics discussed in Australian parliamentary speeches annually.
 This approach allows us to track changes in political priorities and public policy discussions across different governments and time periods.
